### 2018-10-11 README.Rmd
Quick Upload

---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# areal

While methods to interpolate multiple spatial data sets are currently available in the ArcGIS Suite and the `R` package `sf`, `areal` offers an intuitive assortment of options to validate, interpolate, and compare fields between a source and target data set.

## Installation

The best way to install the released version of areal is from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("areal")
```

The development version of `areal` can be accessed from Github with `devtools`:

``` r
# install.packages("devtools")
devtools::install_github("charlie-revord/areal")
```

## Usage

`areal` is split into several different utilities that include: validation of source and target data  (specifically tests for sf object status, shared area unit type, and shared coordinate system), unit type conversion, intersection of source and target data, source field weight calculation, and target field calculation based off source field weight.

## Basic Use

The following showcases the capabilities of `areal` given that the source and target data

### 2018-10-15 README.Rmd
readme update

@@
 
-## Basic Use
+## General Use
 
-The following showcases the capabilities of `areal` given that the source and target data
+The following showcases the capabilities of `areal` given that the source and target data are loaded in by the user alongside the package dependencies.
+The data is hypothetical and named "source" and "target" respectively.
+
+```r
+# load the areal package
+library(areal)
+
+# generate result of SF comparison test
+sf_result <- aw_validate_sf(source, target)
+
+# generate result of unit comparision test
+units_result <- aw_validate_units(source, target)
+
+# generate result of coordinate test
+crs_result <- aw_validate_crs(source,target)
+
+# generate complete result of validation checks
+validate_result <- aw_validate_data(source,target)
+
+# intersect source and target shapefiles and generate
+# geometric area
+intersection <- aw_intersect(source, target)
+
+# aggregate geometric area by source ID
+intersection <- aw_total_id_area(intersection)
+
+# create source area weight field
+intersection <- aw_area_wght(intersection)
+
+# create new interest variable based on area weight
+intersection <- aw_popnew(intersection)
+
+# aggregate new interest variable to target ID
+final_target <- aw_aggregate(intersection)
+```
+
+## Use Collective Function
+
+All of the main functions' tasks can be performed in the encompassing function `aw_interpolate()`. Its use can be seen as follows:
+
+```r
+aw_interpolate(source, target, intersection)
+```
+
+## Additional Documentation
+
+See the package websites and vignettes. The help files can be viewed within R:
+
+```r
+?aw_interpolate
+```
+
+## About the Authors
+
+Charlie Revord was the chef man of this package.
+
+Christopher Prener, Ph.D. contributed to the development of this package. He is a jedi master.

### 2018-12-07 R/aw_interpolate.R
working iternation

@@ -3,7 +3,7 @@
 #' @export
 aw_interpolate <- function(.data, tid, source, sid, ...){
 
-  args <- c(...)
+  args <- rlang::list2(...)
 
   # save parameters to list
   paramList <- as.list(match.call())
@@ -41,29 +41,46 @@ aw_interpolate <- function(.data, tid, source, sid, ...){
 
   } else if (length(args) == 1) {
 
+    # store argument as scalar
+    value <- args[[1]]
+
     # nse
-    if (!is.character(args)) {
-      valueQ <- rlang::enquo(args)
-    } else if (is.character(args)) {
-      valueQ <- rlang::quo(!! rlang::sym(args))
+    if (!is.character(value)) {
+      valueQ <- rlang::enquo(value)
+    } else if (is.character(value)) {
+      valueQ <- rlang::quo(!! rlang::sym(value))
     }
 
-    valueQN <- rlang::quo_name(rlang::enquo(args))
+    valueQN <- rlang::quo_name(rlang::enquo(valueQ))
 
     # strip source and target dataframes
     sourceS <- aw_strip_df(source, id = sidQN, vals = valueQN)
     targetS <- aw_strip_df(.data, id = tidQN)
 
     # interpolate
-    out <- aw_interpolater(source = sourceS, sid = !!sidQ, value = !!valueQ, target = targetS, tid = !!tidQ)
+    out <- aw_interpolater(source = sourceS, sid = !!sidQ, value = !!valueQ, target = targetS,
+                           tid = !!tidQ, class = "sf")
 
   } else if (length(args) > 1) {
 
+    # convert dots list to vector
+    values <- unlist(args, recursive = TRUE)
+    vars <- c(tidQN, values)
 
+    # strip target dataframe
+    targetS <- aw_strip_df(.data, id = tidQN)
 
-  } else {
+    # create list of sf objects
+    values %>%
+      split(values) %>%
+      purrr::map(~ dplyr::select(source, !!sidQ, .x)) %>%
+      purrr::imap(~ aw_interpolater(source = .x, sid = !!sidQ, value = (!!rlang::quo(!! rlang::sym(.y))),
+                                    target = targetS, tid = !!tidQ, class = "tibble")) %>%
+      purrr::reduce(.f = dplyr::bind_cols) %>%
+      dplyr::select(dplyr::one_of(vars)) -> data
 
-    out <- FALSE
+    # left join with target data
+    out <- dplyr::left_join(.data, data, by = tidQN)
 
   }
 
[…]

### 2018-12-07 inst/extdata/functionTest.R

@@ -10,4 +10,8 @@ wards <- stlWards
 
 aw_interpolate(wards, tid = WARD, source = race, sid = "GEOID", "TOTAL_E")
 
+aw_interpolate(wards, tid = WARD, source = race, sid = "GEOID", "TOTAL_E", "WHITE_E")
+
 aw_interpolater(source = race, sid = "GEOID", value = "TOTAL_E", target = wards, tid = WARD)
+
+x <- aw_interpolate(wards, tid = WARD, source = race, sid = "GEOID", "TOTAL_E", "WHITE_E")

### 2018-12-07 inst/extdata/createData.R
add nuisance var to wards data

@@ -24,7 +24,7 @@ left_join(stlTracts, stlRace, by = "GEOID") %>%
   st_transform(crs = 26915) -> stlRace
 
 st_read("inst/extdata/STL_POLITICS_Wards10.shp", stringsAsFactors = FALSE) %>%
-  select(WARD10, Shape_Area) %>%
+  select(-Shape_Leng) %>%
   rename(AREA = Shape_Area,
          WARD = WARD10) %>%
   st_transform(crs = 26915) -> stlWards

### 2018-12-07 README.Rmd
initial README development

--- 2018-10-11 README.Rmd
@@
 ```
+
 # areal
-
 While methods to interpolate multiple spatial data sets are currently available in the ArcGIS Suite and the `R` package `sf`, `areal` offers an intuitive assortment of options to validate, interpolate, and compare fields between a source and target data set.
@@
 ## Installation
-
-The best way to install the released version of areal is from [CRAN](https://CRAN.R-project.org) with:
+The development version of `areal` can be accessed from Github with `remotes`:
 
 ``` r
-install.packages("areal")
-```
-
-The development version of `areal` can be accessed from Github with `devtools`:
-
-``` r
-# install.packages("devtools")
-devtools::install_github("charlie-revord/areal")
+# install.packages("remotes")
+remotes::install_github("slu-openGIS/areal")
 ```
@@
 ## Usage 
+The package contains two overlapping data sets, `stlRace` (2017 ACS demographic counts at the census tract level; $n=106$) and `stlWards` (the 2010 political subdivisions in St.
+Louis; $n=28$).
+These can be used to illustrate the core functionality of the package.
 
-`areal` is split into several different utilities that include: validation of source and target data  (specifically tests for sf object status, shared area unit type, and shared coordinate system), unit type conversion, intersection of source and target data, source field weight calculation, and target field calculation based off source field weight.
+The basic usage of `areal` is through the `aw_interpolate()` function.
+One advantage of `areal` is that it allows for multiple values to be interpolated at a time.
+Here, both total estiatmed population (`TOTAL_E`) and the estimated count of white residents (`WHITE_E`) are interpolated at once:
 
-## Basic Use
+```r
+> library(areal)
+>
+> race <- stlRace
+> wards <- stlWards
+>
+> aw_interpolate(wards, tid = WARD, source = race, sid = "GEOID", output = "tibble", "TOTAL_E", "WHITE_E")
+# A tibble: 28 x 4
+    WARD       AREA TOTAL_E WHITE_E
+ * <int>      <dbl>   <dbl>   <dbl>
+ 1     1  46138761.   7992.    153.
+ 2     2 267817711.  12145.   1323.
+ 3     3  66291644.   7344.    591.
+ 4     4  53210707.   8458.    160.
+ 5     5  60462396.   8783.   1526.
+ 6     6  64337271.  14050.   5840.
+ 7     7 101268146.  15840.   8220.
+ 8     8  45966410.  12188.   7604.
+ 9     9  73993891.  14217.   6838.
+10    10  62915358.  11239.   8703.
+# ... with 18 more rows
+```
 
-The following showcases the capabilities of `areal` given that the source and target data
+One key advantage of `areal` is that is pipeable, meaning that it can fit easily into existing `tidyverse` workflows:
+
+```r
+> wards %>%
++ select(-OBJECTID, -AREA) %>%
++ aw_interpolate(tid = WARD, source = race, sid = "GEOID", output = "tibble", "TOTAL_E", "WHITE_E")
+# A tibble: 28 x 3
+    WARD TOTAL_E WHITE_E
+ * <int>   <dbl>   <dbl>
+ 1     1   7992.    153.
+ 2     2  12145.   1323.
+ 3     3   7344.    591.
+ 4     4   8458.    160.
+ 5     5   8783.   1526.
+ 6     6  14050.   5840.
+ 7     7  15840.   8220.
+ 8     8  12188.   7604.
+ 9     9  14217.   6838.
+10    10  11239.   8703.
+# ... with 18 more rows
+```
+
+Another advantage of `areal` is that the interpolation process is not a "black box", but rather can be manually completed if necessary. Details on this are available on the package's website.

### 2018-12-07 R/aw_interpolate.R

@@ -1,7 +1,7 @@
 #' Interpolate
 #'
 #' @export
-aw_interpolate <- function(.data, tid, source, sid, ...){
+aw_interpolate <- function(.data, tid, source, sid, output = "sf", ...){
 
   args <- rlang::list2(...)
 
@@ -58,7 +58,7 @@ aw_interpolate <- function(.data, tid, source, sid, ...){
     targetS <- aw_strip_df(.data, id = tidQN)
 
     # interpolate
-    out <- aw_interpolater(source = sourceS, sid = !!sidQ, value = !!valueQ, target = targetS,
+    est <- aw_interpolater(source = sourceS, sid = !!sidQ, value = !!valueQ, target = targetS,
                            tid = !!tidQ, class = "sf")
 
   } else if (length(args) > 1) {
@@ -80,7 +80,19 @@ aw_interpolate <- function(.data, tid, source, sid, ...){
       dplyr::select(dplyr::one_of(vars)) -> data
 
     # left join with target data
-    out <- dplyr::left_join(.data, data, by = tidQN)
+    est <- dplyr::left_join(.data, data, by = tidQN)
+
+  }
+
+  # structure output
+  if (output == "sf"){
+
+    out <- est
+
+  } else if (output == "tibble"){
+
+    sf::st_geometry(est) <- NULL
+    out <- dplyr::as_tibble(est)
 
   }
 

### 2018-12-07 inst/extdata/functionTest.R

@@ -10,7 +10,7 @@ wards <- stlWards
 
 aw_interpolate(wards, tid = WARD, source = race, sid = "GEOID", "TOTAL_E")
 
-aw_interpolate(wards, tid = WARD, source = race, sid = "GEOID", "TOTAL_E", "WHITE_E")
+aw_interpolate(wards, tid = WARD, source = race, sid = "GEOID", output = "tibble", "TOTAL_E", "WHITE_E")
 
 aw_interpolater(source = race, sid = "GEOID", value = "TOTAL_E", target = wards, tid = WARD)
 

### 2018-12-07 README.Rmd
updates to README

@@
 ## Usage 
-The package contains two overlapping data sets, `stlRace` (2017 ACS demographic counts at the census tract level; $n=106$) and `stlWards` (the 2010 political subdivisions in St.
-Louis; $n=28$).
+The package contains two overlapping data sets, `stlRace` (2017 ACS demographic counts at the census tract level; *n* = 106) and `stlWards` (the 2010 political subdivisions in St.
+Louis; *n* = 28).
 These can be used to illustrate the core functionality of the package.
@@
 > aw_interpolate(wards, tid = WARD, source = race, sid = "GEOID", output = "tibble", "TOTAL_E", "WHITE_E")
-# A tibble: 28 x 4
-    WARD       AREA TOTAL_E WHITE_E
- * <int>      <dbl>   <dbl>   <dbl>
- 1     1  46138761.   7992.    153.
- 2     2 267817711.  12145.   1323.
- 3     3  66291644.   7344.    591.
- 4     4  53210707.   8458.    160.
- 5     5  60462396.   8783.   1526.
- 6     6  64337271.  14050.   5840.
- 7     7 101268146.  15840.   8220.
- 8     8  45966410.  12188.   7604.
- 9     9  73993891.  14217.   6838.
-10    10  62915358.  11239.   8703.
+# A tibble: 28 x 5
+   OBJECTID  WARD       AREA TOTAL_E WHITE_E
+ *    <dbl> <int>      <dbl>   <dbl>   <dbl>
+ 1        1     1  46138761.   7992.    153.
+ 2        2     2 267817711.  12145.   1323.
+ 3        3     3  66291644.   7344.    591.
+ 4        4     4  53210707.   8458.    160.
+ 5        5     5  60462396.   8783.   1526.
+ 6        6     6  64337271.  14050.   5840.
+ 7        7     7 101268146.  15840.   8220.
+ 8        8     8  45966410.  12188.   7604.
+ 9        9     9  73993891.  14217.   6838.
+10       10    10  62915358.  11239.   8703.
 # ... with 18 more rows
+```
+
+Output can also be generated as an `sf` object:
+
+```r
+> aw_interpolate(wards, tid = WARD, source = race, sid = "GEOID", output = "sf", "TOTAL_E", "WHITE_E")
+Simple feature collection with 28 features and 5 fields
+geometry type:  POLYGON
+dimension:      XY
+bbox:           xmin: 733361.8 ymin: 4268336 xmax: 746157.7 ymax: 4295504
+epsg (SRID):    26915
+proj4string:    +proj=utm +zone=15 +ellps=GRS80 +towgs84=0,0,0,0,0,0,0 +units=m +no_defs
+First 10 features:
+   OBJECTID WARD      AREA   TOTAL_E   WHITE_E                       geometry
+1         1    1  46138761  7991.565  152.8048 POLYGON ((740184.2 4286431,...
+2         2    2 267817711 12145.021 1322.5611 POLYGON ((742392.1 4289178,...
+3         3    3  66291644  7344.287  590.8869 POLYGON ((742956.1 4284113,...
+4         4    4  53210707  8457.672  159.5703 POLYGON ((739557.6 4284080,...
+5         5    5  60462396  8783.377 1526.4801 POLYGON ((744883.8 4281632,...
+6         6    6  64337271 14050.399 5839.8580 POLYGON ((742501.6 4279976,...
+7         7    7 101268146 15840.086 8219.5345 POLYGON ((745618.6 4279867,...
+8         8    8  45966410 12188.131 7604.0605 POLYGON ((739842.8 4277724,...
+9         9    9  73993891 14217.149 6838.4790 POLYGON ((742619.4 4276734,...
+10       10   10  62915358 11239.213 8703.4514 POLYGON ((737257.7 4277050,...
 ```

### 2018-12-07 R/aw_intersect.R
additional R CMD check issues addressed

@@ -63,6 +63,9 @@ aw_intersect <- function(.data, source, areaVar) {
 #'
 aw_area <- function(.data, areaVar){
 
+  # undefined global variables note
+  geometry = NULL
+
   # save parameters to list
   paramList <- as.list(match.call())
 

### 2018-12-07 R/aw_validate.R

@@ -152,7 +152,7 @@ aw_validate_units <- function(source, target){
     # if both objects share same unit type
     out <- TRUE
 
-  } else if(source_unit_type != tracts_unit_type) {
+  } else if(source_unit_type != target_unit_type) {
 
     # if there are not shared units
     out <- FALSE

### 2018-12-07 R/aw_interpolate.R
update docs for aw_verify

@@ -248,7 +248,7 @@ aw_interpolater <- function(source, sid, value, target, tid, class) {
     aw_aggregate(target = target, tid = !!tidQ, newVar = !!valueQ) -> out
 
   # verify result
-  verify <- aw_verify(source = source, result = out, value = valueQN)
+  verify <- aw_verify(source = source, sourceValue = valueQN, result = out, resultValue = valueQN)
 
   if (verify == FALSE){
 

### 2018-12-07 R/aw_verify.R

@@ -1,13 +1,28 @@
 #' Verify Correct Interpolation
 #'
+#' @details \code{aw_verify} ensures that the sum of the resulting interpolated
+#'     value is equal to the sum of the origina source value.
+#'
+#' @usage aw_verify(source, sourceValue, result, resultValue)
+#'
+#' @param source A \code{sf} object with data to be interpolated
+#' @param sourceValue A column within \code{source} to be interpolated
+#' @param result A \code{sf} object with interpolated data
+#' @param resultValue A column within \code{result} with the interpolated values
+#'
+#' @return A logical scalar; if \code{TRUE}, these two values are equal.
+#'
 #' @export
-aw_verify <- function(source, result, value){
+aw_verify <- function(source, sourceValue, result, resultValue){
 
-  sourceSum <- sum(source[[value]])
-  resultSum <- sum(result[[value]])
+  # store sum of original and interpolated values
+  sourceSum <- sum(source[[sourceValue]])
+  resultSum <- sum(result[[resultValue]])
 
+  # logic test
   out <- sourceSum == resultSum
 
+  # return output
   return(out)
 
 }

### 2018-12-07 R/aw_aggregate.R
as usage lines to exported functions' docs

@@ -4,6 +4,8 @@
 #'     based on the target id. These are then joined with the target data. This is
 #'     the fourth step in the interpolation process after \link{aw_weight}.
 #'
+#' @usage aw_aggregate(.data, target, tid, newVar)
+#'
 #' @param .data A given intersected dataset
 #' @param target A \code{sf} object that data should be interpolated to
 #' @param tid A unique identification number within \code{target}

### 2018-12-07 R/aw_calculate.R

@@ -3,6 +3,8 @@
 #' @description \code{aw_calculate} multiplies the given \code{value} by the area weight. This
 #'     is the fourth step in the interpolation process after \link{aw_weight}.
 #'
+#' @usage aw_calculate(.data, value, areaWeight, newVar)
+#'
 #' @param .data A given intersected dataset
 #' @param value A column within \code{source} to be interpolated
 #' @param areaWeight The name of the variable containg area weight per feature

### 2018-12-07 R/aw_interpolate.R

@@ -4,6 +4,8 @@
 #'     data sources and validates them before interpolating one or more listed values
 #'     from the source data into the target data.
 #'
+#' @usage aw_interpolate(.data, tid, source, sid, output = "sf", ...)
+#'
 #' @details Areal weighted interpolation can be used for generating demographic
 #'     estimates for overlapping but incongruent polygon features. It assumes that
 #'     individual members of a population are evenly dispersed within the source features

### 2018-12-07 R/aw_intersect.R

@@ -5,6 +5,8 @@
 #'     with whatever project the data are currently in. This is the first step in the
 #'     interpolation process after data validation and subsetting.
 #'
+#' @usage aw_intersect(.data, source, areaVar)
+#'
 #' @param .data A \code{sf} object that data should be interpolated to
 #' @param source A \code{sf} object with data to be interpolated
 #' @param areaVar The name of the new area variable to be calculated.

### 2018-12-07 R/aw_sum.R

@@ -4,6 +4,8 @@
 #'     the total area by \code{source} id. This is the second step in the
 #'     interpolation process after \link{aw_intersect}.
 #'
+#' @usage aw_sum(.data, sid, areaVar, totalVar)
+#'
 #' @param .data A \code{sf} object that has been intersected using \link{aw_intersect}
 #' @param sid A unique identification number within \code{source}
 #' @param areaVar The name of the variable measuring a feature's area, which is

### 2018-12-07 R/aw_validate.R

@@ -1,7 +1,9 @@
 #' Valdating Data for Interpolation
 #'
 #' @description \code{aw_validate} executes a series of logic tests for \code{sf} object status,
-#' shared unit types, and shared coordinates between source and target data.
+#'     shared unit types, and shared coordinates between source and target data.
+#'
+#' @usage aw_validate(source, target, verbose = FALSE)
 #'
 #' @param source A \code{sf} object with data to be interpolated
 #' @param target A \code{sf} object that data should be interpolated to

### 2018-12-07 R/aw_weight.R

@@ -4,6 +4,8 @@
 #'     field by the total area field. This is the third step in the interpolation
 #'     process after \link{aw_sum}.
 #'
+#' @usage aw_weight(.data, areaVar, totalVar, areaWeight)
+#'
 #' @param .data A \code{sf} object that has been intersected using \link{aw_intersect}
 #' @param areaVar The name of the variable measuring a feature's area
 #' @param totalVar The name of the variable containg total area field by \code{source} id

### 2018-12-07 R/aw_stl_race.R
update data objects

@@ -1,0 +1,45 @@
+#' Race in St. Louis by Census Tract, 2017
+#'
+#' @description A simple features data set containing the geometry and associated attributes
+#'     for the 2013-2017 American Community Survey estimates for race in St. Louis.
+#'
+#' @docType data
+#'
+#' @usage data(aw_stl_race)
+#'
+#' @format A data frame with 106 rows and 24 variables:
+#' \describe{
+#'   \item{GEOID}{full GEOID string}
+#'   \item{STATEFP}{state FIPS code}
+#'   \item{COUNTYFP}{county FIPS code}
+#'   \item{TRACTCE}{tract FIPS code}
+#'   \item{NAMELSAD}{tract name}
+#'   \item{ALAND}{area of tract land, square meters}
+#'   \item{AWATER}{area of tract water, square meters}
+#'   \item{TOTAL_E}{total populaton count, estimated}
+#'   \item{TOTAL_M}{total populaton count, margin of error}
+#'   \item{WHITE_E}{white populaton count, estimated}
+#'   \item{WHITE_M}{white populaton count, margin of error}
+#'   \item{BLACK_E}{black populaton count, estimated}
+#'   \item{BLACK_M}{black populaton count, margin of error}
+#'   \item{AIAN_E}{american indian and alskan native populaton count, estimated}
+#'   \item{AIAN_M}{american indian and alskan native populaton count, margin of error}
+#'   \item{ASIAN_E}{asian populaton count, estimated}
+#'   \item{ASIAN_M}{asian populaton count, margin of error}
+#'   \item{NHPI_E}{native hawaiian and pacific islander populaton count, estimated}
+#'   \item{NHPI_M}{native hawaiian and pacific islander populaton count, margin of error}
+#'   \item{OTHER_E}{other race populaton count, estimated}
+#'   \item{OTHER_M}{other race populaton count, margin of error}
+#'   \item{TWOPLUS_E}{two or more races populaton count, estimated}
+#'   \item{TWOPLUS_M}{two or more races populaton count, margin of error}
+#'   \item{geometry}{simple features geometry}
+#'   }
+#'
+#' @source \link{tidycensus} package
+#'
+#' @examples
+#' str(aw_stl_race)
+#' head(aw_stl_race)
+#' summary(aw_stl_race$ALAND)
+#'
+"aw_stl_race"

### 2018-12-07 R/aw_stl_wards.R

@@ -1,0 +1,27 @@
+#' Ward Boundaries in St. Louis, 2010
+#'
+#' @description A simple features data set containing the 2010 Ward boundaries, which
+#'     are used as districts for Alderpersons who serve as elected representatives.
+#'     The \code{OBJECTID} and \code{AREA} columns are included to simulate "real"
+#'     data that may have superfluous or unclear columns.
+#'
+#' @docType data
+#'
+#' @usage data(aw_stl_wards)
+#'
+#' @format A data frame with 28 rows and 4 variables:
+#' \describe{
+#'   \item{OBJECTID}{Artifact from ESRI data creation}
+#'   \item{WARD}{Ward number}
+#'   \item{AREA}{area of each ward}
+#'   \item{geometry}{simple features geometry}
+#'   }
+#'
+#' @source City of St. Louis
+#'
+#' @examples
+#' str(aw_stl_wards)
+#' head(aw_stl_wards)
+#' summary(aw_stl_wards$AREA)
+#'
+"aw_stl_wards"

### 2018-12-07 inst/extdata/createData.R

@@ -15,21 +15,22 @@ get_acs(geography = "tract", state = 29, county = 510, year = 2017, table = "B02
          ASIAN_E = B02001_005E, ASIAN_M = B02001_005M,
          NHPI_E = B02001_006E, NHPI_M = B02001_006M,
          OTHER_E = B02001_007E, OTHER_M = B02001_007M,
-         TWOPLUS_E = B02001_008E, TWOPLUS_M = B02001_008M) -> stlRace
+         TWOPLUS_E = B02001_008E, TWOPLUS_M = B02001_008M) %>%
+  select(-B02001_009E, -B02001_009M, -B02001_010E, -B02001_010M) -> stlRace
 
 tracts(state = 29, county = 510, class = "sf") %>%
   select(GEOID, STATEFP, COUNTYFP, TRACTCE, NAMELSAD, ALAND, AWATER) -> stlTracts
 
 left_join(stlTracts, stlRace, by = "GEOID") %>%
-  st_transform(crs = 26915) -> stlRace
+  st_transform(crs = 26915) -> aw_stl_race
 
 st_read("inst/extdata/STL_POLITICS_Wards10.shp", stringsAsFactors = FALSE) %>%
   select(-Shape_Leng) %>%
   rename(AREA = Shape_Area,
          WARD = WARD10) %>%
-  st_transform(crs = 26915) -> stlWards
+  st_transform(crs = 26915) -> aw_stl_wards
 
-use_data(stlRace, overwrite = TRUE)
-use_data(stlWards, overwrite = TRUE)
+use_data(aw_stl_race, overwrite = TRUE)
+use_data(aw_stl_wards, overwrite = TRUE)
 
-rm(stlRace, stlTracts, stlWards)
+rm(stlTracts, aw_stl_race, aw_stl_wards)

### 2018-12-07 README.Rmd
update object names in README

@@
 >
-> race <- stlRace
-> wards <- stlWards
+> race <- aw_stl_race
+> wards <- aw_stl_wards
 >

### 2018-12-07 R/aw_stl_race.R
and we're passing R CMD checkgit add -A

@@ -35,7 +35,7 @@
 #'   \item{geometry}{simple features geometry}
 #'   }
 #'
-#' @source \link{tidycensus} package
+#' @source \code{tidycensus} package
 #'
 #' @examples
 #' str(aw_stl_race)

### 2018-12-07 README.Rmd
add hex and badges to README

@@
 
-# areal
+# areal <img src="man/figures/arealLogo.png" align="right" />
+
+[![lifecycle](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://www.tidyverse.org/lifecycle/#maturing)
+[![CRAN_status_badge](http://www.r-pkg.org/badges/version/areal)](https://cran.r-project.org/package=areal)
+
 While methods to interpolate multiple spatial data sets are currently available in the ArcGIS Suite and the `R` package `sf`, `areal` offers an intuitive assortment of options to validate, interpolate, and compare fields between a source and target data set.

### 2018-12-14 R/aw_interpolate.R
rename aw_sum to aw_total, add clipped data

@@ -384,7 +384,7 @@ aw_strip_df <- function(.data, id, value){
 #' Carry Out Interpolation
 #'
 #' @description \code{aw_interpolater} performs pipeline of interpolation specific
-#'     calculations with \code{aw_intersect}, \code{aw_sum}, \code{aw_weight},
+#'     calculations with \code{aw_intersect}, \code{aw_total}, \code{aw_weight},
 #'     \code{aw_calculate}, and \code{aw_aggregate}. The interpolated total is then
 #'     verified against the total calculated from the source data using \code{aw_verify}.
 #'
@@ -445,24 +445,17 @@ aw_interpolater <- function(source, sid, value, target, tid, type, weight, class
 
     target %>%
       aw_intersect(source = source, areaVar = "...area") %>%
-      aw_sum(source = source, id = !!sidQ, areaVar = "...area", totalVar = "...totalArea",
+      aw_total(source = source, id = !!sidQ, areaVar = "...area", totalVar = "...totalArea",
              type = "extensive", weight = weight) %>%
       aw_weight(areaVar = "...area", totalVar = "...totalArea", areaWeight = "...areaWeight") %>%
       aw_calculate(value = !!valueQ, areaWeight = "...areaWeight", newVar = !!valueQ) %>%
       aw_aggregate(target = target, tid = !!tidQ, newVar = !!valueQ) -> Interpolated.Data.Out
 
-    # verify result
-    # if (aw_verify(source = source, sourceValue = !!valueQ, result = Interpolated.Data.Out, resultValue = !!valueQ) == FALSE){
-
-    #  warning("Possibly problematic interpolation result - the sum of the result's value does not equal the sum of the source's value.")
-
-    # }
-
   } else if (type == "intensive"){
 
     target %>%
       aw_intersect(source = source, areaVar = "...area") %>%
-      aw_sum(source = source, id = !!tidQ, areaVar = "...area", totalVar = "...totalArea",
+      aw_total(source = source, id = !!tidQ, areaVar = "...area", totalVar = "...totalArea",
              weight = weight, type = "intensive") %>%
       aw_weight(areaVar = "...area", totalVar = "...totalArea", areaWeight = "...areaWeight") %>%
       aw_calculate(value = !!valueQ, areaWeight = "...areaWeight", newVar = !!valueQ) %>%

### 2018-12-14 R/aw_stl_wardsClipped.R

@@ -1,0 +1,24 @@
+#' Clipped Ward Boundaries in St. Louis, 2010
+#'
+#' @description A simple features data set containing the 2010 Ward boundaries, which
+#'     are used as districts for Alderpersons who serve as elected representatives.
+#'     This version of the ward boundary has been modified so that the wards only
+#'     extend to the Mississippi River shoreline.
+#'
+#' @docType data
+#'
+#' @usage data(aw_stl_wardsClipped)
+#'
+#' @format A data frame with 28 rows and 2 variables:
+#' \describe{
+#'   \item{WARD}{Ward number}
+#'   \item{geometry}{simple features geometry}
+#'   }
+#'
+#' @source City of St. Louis
+#'
+#' @examples
+#' str(aw_stl_wardsClipped)
+#' head(aw_stl_wardsClipped)
+#'
+"aw_stl_wardsClipped"

### 2018-12-14 R/aw_total.R

@@ -1,10 +1,10 @@
 #' Create new total area field in intersection
 #'
-#' @description \code{aw_sum} produces a new total area field that contains
+#' @description \code{aw_total} produces a new total area field that contains
 #'     the total area by \code{source} id. This is the second step in the
 #'     interpolation process after \link{aw_intersect}.
 #'
-#' @usage aw_sum(.data, source, id, areaVar, totalVar, type, weight)
+#' @usage aw_total(.data, source, id, areaVar, totalVar, type, weight)
 #'
 #' @param .data A \code{sf} object that has been intersected using \link{aw_intersect}
 #' @param source A \code{sf} object with data to be interpolated
@@ -32,7 +32,7 @@
 #' @importFrom sf st_geometry
 #'
 #' @export
-aw_sum <- function(.data, source, id, areaVar, totalVar, type, weight){
+aw_total <- function(.data, source, id, areaVar, totalVar, type, weight){
 
   # save parameters to list
   paramList <- as.list(match.call())

### 2018-12-14 R/aw_weight.R

@@ -92,15 +92,6 @@ aw_weight <- function(.data, areaVar, totalVar, areaWeight){
 
   }
 
-  if (!!areaWeightQN != "...areaWeight"){
-
-    if(!!areaWeightQN %in% colnames(.data) == FALSE) {
-      stop(glue::glue("Variable '{var}', given for the area weight, cannot be found in the given intersected object.",
-                      var = areaWeightQ))
-    }
-
-  }
-
   if (!!totalVarQN != "...totalArea"){
 
     if(!!totalVarQN %in% colnames(.data) == FALSE) {

### 2018-12-14 inst/extdata/functionTest.R

@@ -17,7 +17,7 @@ aw_interpolate(wards, tid = WARD, source = race2, sid = "GEOID", output = "tibbl
 
 wards %>%
   select(-OBJECTID, -AREA) %>%
-  aw_interpolate(tid = WARD, source = race, sid = "GEOID", type = "extensive", output = "sf",
+  aw_interpolate(tid = WARD, source = race, sid = "GEOID", type = "extensive", weight = "sum", output = "sf",
                  "TOTAL_E", "WHITE_E", "BLACK_E")
 
 aw_interpolate(wards, tid = WARD, source = race, sid = "GEOID", type = "extensive", output = "sf", "TOTAL_E")

### 2018-12-14 R/aw_interpolate.R
add tool for previewing weights

@@ -43,6 +43,7 @@
 #' @importFrom dplyr bind_cols
 #' @importFrom dplyr left_join
 #' @importFrom dplyr one_of
+#' @importFrom dplyr select
 #' @importFrom glue glue
 #' @importFrom purrr imap
 #' @importFrom purrr map

### 2018-12-14 R/aw_preview_weights.R

@@ -1,0 +1,210 @@
+#' Preview Areal Weights
+#'
+#' @description Provides a preview of the weight options for areal weighted interpolation.
+#'     This can be useful for selecting the final specification for \code{aw_interpolate}
+#'     without having to construct a pipeline of all of the subfunctions manually.
+#'
+#' @usage aw_preview_weights(.data, tid, source, sid, type)
+#'
+#' @param .data A \code{sf} object that data should be interpolated to (this is referred
+#'     to as the \code{target} elsewhere in the package).
+#' @param tid A unique identification number within \code{target}
+#' @param source A \code{sf} object with data to be interpolated
+#' @param sid A unique identification number within \code{source}
+#' @param type One of either \code{"extensive"} (if the data are spatitally extensive e.g.
+#'     population counts), \code{"intensive"} (if the data are spatially intensive e.g.
+#'     population density), or \code{"mixed"} (if the data include both extensive and
+#'     intensive values). If \code{"extensive"}, the sum is returned for the interpolated
+#'     value. If \code{"intensive"}, the mean is returned for the interpolated value.
+#'     If \code{"mixed"}, vectors named \code{"extensive"} and \code{"intensive"} containing
+#'     the relevant variable names should be specified in the dots.
+#'
+#' @return A tibble with the areal weights that would be used for interpolation if \code{type}
+#'     is either \code{"extensive"} or \code{"intensive"}. If it is mixed, two tibbles (one for
+#'     \code{"extensive"} and one for \code{"intensive"}) are returned as a list.
+#'
+#' @importFrom dplyr left_join
+#' @importFrom glue glue
+#' @importFrom rlang enquo
+#' @importFrom rlang quo
+#' @importFrom rlang quo_name
+#' @importFrom rlang sym
+#'
+#' @export
+aw_preview_weights <- function(.data, tid, source, sid, type){
+
+  # save parameters to list
+  paramList <- as.list(match.call())
+
+  # check for missing parameters
+  if (missing(tid)) {
+    stop("A variable name must be specified for the 'tid' argument.")
+  }
+
+  if (missing(source)) {
+    stop("A sf object must be specified for the 'source' argument.")
+  }
[…]

### 2018-12-14 R/aw_validate.R

@@ -55,7 +55,7 @@ aw_validate <- function(source, target, varList, verbose = FALSE){
 
   }
 
-  # store results from all three validate subfunctions
+  # store results from primary validate subfunctions
   sf_result <- aw_validate_sf(source, target)
 
   # execute additional tests if both are sf, otherwise set results to NA
@@ -117,6 +117,86 @@ aw_validate <- function(source, target, varList, verbose = FALSE){
                "Overall Evaluation"),
       result = c(sf_result, crs_result, unit_result, longlat_result, vars_exist_result,
                  vars_conflict_result, result),
+      stringsAsFactors = FALSE)
+
+    out <- as_tibble(table)
+  }
+
+  # return output
+  return(out)
+
+}
+
+#' Lite Version of Validation for aw_preview_weights
+#'
+#' @description \code{aw_validate_preview} is designed to be called by
+#'     \code{aw_preview_weights} before the weights are calculated. It
+#'     lacks the variable validation functionality of \code{aw_validate}.
+#'
+#' @param source A \code{sf} object with data to be interpolated
+#' @param target A \code{sf} object that data should be interpolated to
+#' @param verbose A logical scalar; if \code{TRUE}, a tibble with test results is returned
+#'
+#' @return If \code{verbose} is \code{FALSE}, a logical scalar is returned that is \code{TRUE}
+#'     is all tests are passed and \code{FALSE} if one or more tests is failed. If \code{verbose}
+#'     is \code{TRUE}, a tibble with detailed test results is returned.
+#'
+#' @importFrom glue glue
+#'
+aw_validate_preview <- function(source, target, verbose = FALSE){
+
+  # store results from primary validate subfunctions
+  sf_result <- aw_validate_sf(source, target)
+
+  # execute additional tests if both are sf, otherwise set results to NA
+  if (sf_result == FALSE){
+
+    unit_result <- NA
+    crs_result <- NA
+    longlat_result <- NA
+
+  } else if (sf_result == TRUE){
+
+    # do both source and target have same CRS?
+    crs_result <- aw_validate_crs(source, target)
+
+    # do both source and target have same measurement units?
+    unit_result <- aw_validate_units(source, target)
+
+    # are both source and target CRS values in planar?
+    longlat_result1 <- aw_validate_longlat(source)
+    longlat_result2 <- aw_validate_longlat(target)
+
[…]

### 2018-12-14 R/aw_weight.R

@@ -2,7 +2,7 @@
 #'
 #' @description \code{aw_weight} creates an area weight field by dividing the area
 #'     field by the total area field. This is the third step in the interpolation
-#'     process after \link{aw_sum}.
+#'     process after \link{aw_weight}.
 #'
 #' @usage aw_weight(.data, areaVar, totalVar, areaWeight)
 #'

### 2018-12-14 tests/testthat/test_interpolate.R
update so that unit tests now pass

@@ -3,28 +3,28 @@ context("test aw_interpolate function")
 # load test data ------------------------------------------------
 
 # source data
-race <- aw_stl_race
-asthma <- aw_stl_asthma
+data(aw_stl_race, package = "areal")
+data(aw_stl_asthma, package = "areal")
 
 # target data
-wards <- aw_stl_wards
+data(aw_stl_wards, package = "areal")
 
 # create comparison data
-totalCompare <- sf::st_interpolate_aw(race["TOTAL_E"], wards, extensive = TRUE)
-asthmaCompare <- sf::st_interpolate_aw(asthma["ASTHMA"], wards, extensive = FALSE)
+totalCompare <- sf::st_interpolate_aw(aw_stl_race["TOTAL_E"], aw_stl_wards, extensive = TRUE)
+asthmaCompare <- sf::st_interpolate_aw(aw_stl_asthma["ASTHMA"], aw_stl_wards, extensive = FALSE)
 
 # test errors ------------------------------------------------
 
 # test results ------------------------------------------------
 
-totalResult1 <- aw_interpolate(wards, tid = WARD, source = race, sid = "GEOID", type = "extensive",
-                               weight = "sum", output = "sf", "TOTAL_E")
+totalResult1 <- aw_interpolate(aw_stl_wards, tid = WARD, source = aw_stl_race, sid = "GEOID",
+                               type = "extensive", weight = "sum", output = "sf", "TOTAL_E")
 
-totalResult2 <- aw_interpolate(wards, tid = WARD, source = race, sid = "GEOID", type = "extensive",
-                               weight = "total", output = "sf", "TOTAL_E")
+totalResult2 <- aw_interpolate(aw_stl_wards, tid = WARD, source = aw_stl_race, sid = "GEOID",
+                               type = "extensive", weight = "total", output = "sf", "TOTAL_E")
 
-asthmaResult <- aw_interpolate(wards, tid = WARD, source = asthma, sid = "GEOID", type = "intensive",
-                               output = "sf", weight = "sum", "ASTHMA")
+asthmaResult <- aw_interpolate(aw_stl_wards, tid = WARD, source = aw_stl_asthma, sid = "GEOID",
+                               type = "intensive", output = "sf", weight = "sum", "ASTHMA")
 
 test_that("interpolated values are equal", {
   expect_equal(totalCompare$TOTAL_E, totalResult2$TOTAL_E)

### 2018-12-14 tests/testthat/test_interpolate.R
all main tests now working

@@ -10,8 +10,9 @@ data(aw_stl_asthma, package = "areal")
 data(aw_stl_wards, package = "areal")
 
 # create comparison data
-totalCompare <- sf::st_interpolate_aw(aw_stl_race["TOTAL_E"], aw_stl_wards, extensive = TRUE)
-asthmaCompare <- sf::st_interpolate_aw(aw_stl_asthma["ASTHMA"], aw_stl_wards, extensive = FALSE)
+load(system.file("extdata", "totalCompare1.rda", package = "areal", mustWork = TRUE))
+totalCompare2 <- suppressWarnings(sf::st_interpolate_aw(aw_stl_race["TOTAL_E"], aw_stl_wards, extensive = TRUE))
+asthmaCompare <- suppressWarnings(sf::st_interpolate_aw(aw_stl_asthma["ASTHMA"], aw_stl_wards, extensive = FALSE))
 
 # test errors ------------------------------------------------
 
@@ -27,6 +28,7 @@ asthmaResult <- aw_interpolate(aw_stl_wards, tid = WARD, source = aw_stl_asthma,
                                type = "intensive", output = "sf", weight = "sum", "ASTHMA")
 
 test_that("interpolated values are equal", {
-  expect_equal(totalCompare$TOTAL_E, totalResult2$TOTAL_E)
+  expect_equal(totalCompare1$TOTAL_E, totalResult1$TOTAL_E)
+  expect_equal(totalCompare2$TOTAL_E, totalResult2$TOTAL_E)
   expect_equal(asthmaCompare$ASTHMA, asthmaResult$ASTHMA)
 })

### 2018-12-14 R/aw_preview_weights.R
add object errors to aw_preview_weights

@@ -79,6 +79,20 @@ aw_preview_weights <- function(.data, tid, source, sid, type){
   targetQN <- rlang::quo_name(rlang::enquo(.data))
   sourceQN <- rlang::quo_name(rlang::enquo(source))
 
+  # validate target exists
+  if (targetQN != "." & !exists(targetQN)){
+
+    stop(glue::glue("Object '{targetQN}' not found."))
+
+  }
+
+  # validate source exists
+  if (!exists(sourceQN)) {
+
+    stop(glue::glue("Object '{sourceQN}' not found."))
+
+  }
+
   # check variables
   if(!!sidQN %in% colnames(source) == FALSE) {
     stop(glue::glue("Variable '{var}', given for the source ID ('sid'), cannot be found in the given source object.",

### 2018-12-14 .travis/install.sh
add ci integration

@@ -1,0 +1,38 @@
+#!/bin/bash
+
+if [[ $TRAVIS_OS_NAME == 'linux' ]]; then
+
+  sudo add-apt-repository ppa:ubuntugis/ubuntugis-unstable --yes
+  sudo apt-get --yes --force-yes update -qq
+
+  # install tmap dependencies
+  sudo apt-get install --yes libprotobuf-dev protobuf-compiler libv8-3.14-dev
+
+  # install tmap dependencies; for 16.04 libjq-dev this ppa is needed:
+  sudo add-apt-repository -y ppa:opencpu/jq
+  sudo apt-get --yes --force-yes update -qq
+  sudo apt-get install libjq-dev
+
+  # units/udunits2 dependency:
+  sudo apt-get install --yes libudunits2-dev
+
+  # sf dependencies:
+  sudo apt-get install --yes libproj-dev libgeos-dev libgdal-dev
+
+  # postgis source compile dependencies:
+  sudo apt-get --yes install libjson-c-dev postgresql-server-dev-9.6
+
+  # install postgis from source:
+  wget http://download.osgeo.org/postgis/source/postgis-2.3.2.tar.gz
+  (mv postgis* /tmp; cd /tmp; tar xzf postgis-2.3.2.tar.gz)
+  (cd /tmp/postgis-2.3.2 ; ./configure; make; sudo make install)
+
+  # create postgis databases:
+  sudo service postgresql restart
+  createdb postgis
+  psql -d postgis -c "CREATE EXTENSION postgis;"
+  psql -d postgis -c "GRANT CREATE ON DATABASE postgis TO travis"
+  createdb empty
+  psql -d empty -c "CREATE EXTENSION postgis;"
+
+fi

### 2018-12-14 README.Rmd
add testing badges, code coverage functionality

@@
 [![lifecycle](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://www.tidyverse.org/lifecycle/#maturing)
+[![Travis-CI Build Status](https://travis-ci.org/slu-openGIS/areal?branch=master)](https://travis-ci.org/slu-openGIS/areal)
+[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/slu-openGIS/areal?branch=master&svg=true)](https://ci.appveyor.com/project/chris-prener/areal)
+[![Coverage status](https://codecov.io/gh/slu-openGIS/areal/branch/master/graph/badge.svg)](https://codecov.io/github/slu-openGIS/areal?branch=master)
 [![CRAN_status_badge](http://www.r-pkg.org/badges/version/areal)](https://cran.r-project.org/package=areal)

### 2018-12-14 README.Rmd
fix travis badge

--- 2018-12-07 README.Rmd
@@
 [![lifecycle](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://www.tidyverse.org/lifecycle/#maturing)
+[![Travis-CI Build Status](https://travis-ci.org/slu-openGIS/areal.svg?branch=master)](https://travis-ci.org/slu-openGIS/areal)
+[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/slu-openGIS/areal?branch=master&svg=true)](https://ci.appveyor.com/project/chris-prener/areal)
+[![Coverage status](https://codecov.io/gh/slu-openGIS/areal/branch/master/graph/badge.svg)](https://codecov.io/github/slu-openGIS/areal?branch=master)
 [![CRAN_status_badge](http://www.r-pkg.org/badges/version/areal)](https://cran.r-project.org/package=areal)

### 2018-12-14 README.Rmd
update interpolate process for mixed to resolve weight issue

@@
 )
+
+library(areal)
+library(dplyr)
+library(sf)
+
+data(aw_stl_asthma, package = "areal")
+asthma <- aw_stl_asthma
+
+data(aw_stl_race, package = "areal")
+race <- aw_stl_race
+
+data(aw_stl_wards, package = "areal")
+wards <- aw_stl_wards
 ```
@@
 
-``` r
+```r
 # install.packages("remotes")
@@
 ## Usage 
-The package contains two overlapping data sets, `stlRace` (2017 ACS demographic counts at the census tract level; *n* = 106) and `stlWards` (the 2010 political subdivisions in St.
-Louis; *n* = 28).
+The package contains three overlapping data sets:
+
+* `aw_stl_race` (2017 ACS demographic counts at the census tract level; *n* = 106) 
+* `aw_stl_asthma` (2017 asthma rates at the census tract level; *n* = 106)
+* `aw_stl_wards` (the 2010 political subdivisions in St. Louis; *n* = 28).
+
 These can be used to illustrate the core functionality of the package.
 
-The basic usage of `areal` is through the `aw_interpolate()` function.
-One advantage of `areal` is that it allows for multiple values to be interpolated at a time.
-Here, both total estiatmed population (`TOTAL_E`) and the estimated count of white residents (`WHITE_E`) are interpolated at once:
+The basic usage of `areal` is through the `aw_interpolate()` function, which is illustrated below. The following examples assume:
 
@@
 > race <- aw_stl_race
+> asthma <- aw_stl_asthma
 > wards <- aw_stl_wards
->
-> aw_interpolate(wards, tid = WARD, source = race, sid = "GEOID", output = "tibble", "TOTAL_E", "WHITE_E")
-# A tibble: 28 x 5
-   OBJECTID  WARD       AREA TOTAL_E WHITE_E
- *    <dbl> <int>      <dbl>   <dbl>   <dbl>
- 1        1     1  46138761.   7992.    153.
- 2        2     2 267817711.  12145.   1323.
- 3        3     3  66291644.   7344.    591.
- 4        4     4  53210707.   8458.    160.
- 5        5     5  60462396.   8783.   1526.
- 6        6     6  64337271.  14050.   5840.
- 7        7     7 101268146.  15840.   8220.
- 8        8     8  45966410.  12188.   7604.
- 9        9     9  73993891.  14217.   6838.
-10       10    10  62915358.  11239.   8703.
-# ... with 18 more rows
 ```
 
-Output can also be generated as an `sf` object:
+### Data Validation
+`areal` contains a detailed data validation workflow that ensures that both the `source` and `target` data are compatible with each either. It can be run in a simple format:
 
-```r
-> aw_interpolate(wards, tid = WARD, source = race, sid = "GEOID", output = "sf", "TOTAL_E", "WHITE_E")
-Simple feature collection with 28 features and 5 fields
-geometry type:  POLYGON
-dimension:      XY
-bbox:           xmin: 733361.8 ymin: 4268336 xmax: 746157.7 ymax: 4295504
-epsg (SRID):    26915
-proj4string:    +proj=utm +zone=15 +ellps=GRS80 +towgs84=0,0,0,0,0,0,0 +units=m +no_defs
-First 10 features:
-   OBJECTID WARD      AREA   TOTAL_E   WHITE_E                       geometry
-1         1    1  46138761  7991.565  152.8048 POLYGON ((740184.2 4286431,...
-2         2    2 267817711 12145.021 1322.5611 POLYGON ((742392.1 4289178,...
-3         3    3  66291644  7344.287  590.8869 POLYGON ((742956.1 4284113,...
-4         4    4  53210707  8457.672  159.5703 POLYGON ((739557.6 4284080,...
-5         5    5  60462396  8783.377 1526.4801 POLYGON ((744883.8 4281632,...
-6         6    6  64337271 14050.399 5839.8580 POLYGON ((742501.6 4279976,...
-7         7    7 101268146 15840.086 8219.5345 POLYGON ((745618.6 4279867,...
-8         8    8  45966410 12188.131 7604.0605 POLYGON ((739842.8 4277724,...
-9         9    9  73993891 14217.149 6838.4790 POLYGON ((742619.4 4276734,...
-10       10   10  62915358 11239.213 8703.4514 POLYGON ((737257.7 4277050,...
+```{r validate-simple}
+aw_validate(source = asthma, target = wards, varList = c("ASTHMA"))
 ```
+
+If `aw_validate()` returns a `FALSE` value, it can also be run in a verbose manner that returns a detailed tibble:
+
+```{r validate-verbose}
+aw_validate(source = asthma, target = wards, varList = c("ASTHMA"), verbose = TRUE)
+```
+
+### Built-in Iteration
+
+One advantage of `areal` is that it allows for multiple values to be interpolated at a time.
+Here, both total estiatmed population (`TOTAL_E`), the estimated count of white residents (`WHITE_E`), and the estimated count of African American residents (`BLACK_E`) are interpolated at once:
+
+```{r iteration}
+aw_interpolate(wards, tid = WARD, source = race, sid = "GEOID", type = "extensive", 
+               weight = "sum", output = "tibble", "TOTAL_E", "WHITE_E", "BLACK_E")
+```
+
+### Interpolation Choices
+Both spatially extensive (i.e.
+counts; illustrated in the prior examples) and spatially intensive (i.e.
+ratios) data can be interpolated.
+For spatially intensive data, the average is returned rather than the sum:
+
+```{r intensive}
+aw_interpolate(wards, tid = WARD, source = asthma, sid = "GEOID", type = "intensive", 
+               weight = "sum", output = "tibble", "ASTHMA")
+```
+
+Both extensive and intensive data can be interpolated simultaneously by setting `type` to `"mixed"` and naming two vectors `extensive` and `intensive`.
+These vectors should include the relevent variable names:
+
+```{r mixed}
+# remove sf geometry
+st_geometry(race) <- NULL
+
+# create combined data
+race %>%
+  select(GEOID, TOTAL_E, WHITE_E, BLACK_E) %>%
+  left_join(asthma, ., by = "GEOID") -> combinedData
+
+# interpolate
+aw_interpolate(wards, tid = WARD, source = combinedData, sid = "GEOID", type = "mixed", 
+               weight = "sum", output = "tibble", 
+               extensive = c("TOTAL_E", "WHITE_E", "BLACK_E"),
+               intensive = c("ASTHMA"))
+```
+
+### Output Choices
+Output can be either a tibble (shown in the prior example) or an `sf` object:
+
+```{r sf-output}
+aw_interpolate(wards, tid = WARD, source = race, sid = "GEOID", type = "extensive", 
+               weight = "sum", output = "sf", "TOTAL_E", "WHITE_E", "BLACK_E")
+```
+
+### Pipe Compatible
 
@@
 
-```r
-> wards %>%
-+ select(-OBJECTID, -AREA) %>%
-+ aw_interpolate(tid = WARD, source = race, sid = "GEOID", output = "tibble", "TOTAL_E", "WHITE_E")
-# A tibble: 28 x 3
-    WARD TOTAL_E WHITE_E
- * <int>   <dbl>   <dbl>
- 1     1   7992.    153.
- 2     2  12145.   1323.
- 3     3   7344.    591.
- 4     4   8458.    160.
- 5     5   8783.   1526.
- 6     6  14050.   5840.
- 7     7  15840.   8220.
- 8     8  12188.   7604.
- 9     9  14217.   6838.
-10    10  11239.   8703.
-# ... with 18 more rows
+```{r pipe}
+wards %>%
+  select(-OBJECTID, -AREA) %>%
+  aw_interpolate(tid = WARD, source = race, sid = "GEOID", type = "extensive", 
+               weight = "sum", output = "tibble", "TOTAL_E", "WHITE_E", "BLACK_E")
 ```
 
-Another advantage of `areal` is that the interpolation process is not a "black box", but rather can be manually completed if necessary. Details on this are available on the package's website.
+### Transparent
+
+Another advantage of `areal` is that the interpolation process is not a "black box", but rather can be manually completed if necessary. Details on this will be available on the package's website.

### 2018-12-14 R/aw_interpolate.R

@@ -281,7 +281,7 @@ aw_interpolate <- function(.data, tid, source, sid, type, weight, output, ...){
 
       # interpolate
       intensive <- aw_interpolater(source = sourceS, sid = !!sidQ, value = !!valueQ, target = targetS,
-                                   tid = !!tidQ, type = "intensive", class = "tibble")
+                                   tid = !!tidQ, type = "intensive", weight = "sum", class = "tibble")
 
     } else if (length(args$intensive) > 1){
 
@@ -297,7 +297,7 @@ aw_interpolate <- function(.data, tid, source, sid, type, weight, output, ...){
         split(values) %>%
         purrr::map(~ aw_strip_df(source, id = !!sidQ, value = .x)) %>%
         purrr::imap(~ aw_interpolater(source = .x, sid = !!sidQ, value = (!! rlang::quo(!! rlang::sym(.y))),
-                                      target = targetS, tid = !!tidQ, type = "intensive",
+                                      target = targetS, tid = !!tidQ, type = "intensive", weight = "sum",
                                       class = "tibble")) %>%
         purrr::reduce(.f = dplyr::bind_cols) %>%
         dplyr::select(dplyr::one_of(vars)) -> intensive

### 2018-12-14 README.Rmd
update intro

@@
 
-While methods to interpolate multiple spatial data sets are currently available in the ArcGIS Suite and the `R` package `sf`, `areal` offers an intuitive assortment of options to validate, interpolate, and compare fields between a source and target data set.
+`areal` offers an intuitive assortment of options to validate, interpolate, and compare fields between a source and target data set.
+While methods for implementing areal weighted interpolation are available outside of the `R` ecosystem (ex - toolboxes in ArcGIS) and within `R` (the `sf` package's `st_interpolate_aw`) function, `areal` fills a niche by providing additional functionality not available in `sf` while taking advantage of the reproducibility of `R`.
+
+`areal` currently implents only areal weighted interpolation, but a roadmap is being developed to add additional interpolation methods as well.
+This will be posted on the package's website before the initial CRAN release.
 
 ## Installation
+### Installing Dependencies
+
+You should check the [`sf` package website](https://r-spatial.github.io/sf/) for the latest details on installing dependencies for that package.
+Instructions vary significantly by operating system.
+For best results, have `sf` installed before you install `qualmap`.
+Other dependencies, like `dplyr`, will be installed automatically with `areal` if they are not already present.
+
+### Installing areal
 The development version of `areal` can be accessed from Github with `remotes`:
@@
 # remove sf geometry
-st_geometry(race) <- NULL
+raceTable <- race
+st_geometry(raceTable) <- NULL
 
 # create combined data
-race %>%
+raceTable %>%
   select(GEOID, TOTAL_E, WHITE_E, BLACK_E) %>%
@@
 ```{r sf-output}
-aw_interpolate(wards, tid = WARD, source = race, sid = "GEOID", type = "extensive", 
+aw_interpolate(wards, tid = "WARD", source = race, sid = "GEOID", type = "extensive", 
                weight = "sum", output = "sf", "TOTAL_E", "WHITE_E", "BLACK_E")

### 2018-12-14 R/aw_interpolate.R
updates to api for aw_interpolate based on unit tests

@@ -4,7 +4,8 @@
 #'     data sources and validates them before interpolating one or more listed values
 #'     from the source data into the target data.
 #'
-#' @usage aw_interpolate(.data, tid, source, sid, type, weight, output, ...)
+#' @usage aw_interpolate(.data, tid, source, sid, weight = "sum", output = "sf", extensive,
+#'     intensive)
 #'
 #' @details Areal weighted interpolation can be used for generating demographic
 #'     estimates for overlapping but incongruent polygon features. It assumes that
@@ -17,22 +18,14 @@
 #' @param tid A unique identification number within \code{target}
 #' @param source A \code{sf} object with data to be interpolated
 #' @param sid A unique identification number within \code{source}
-#' @param type One of either \code{"extensive"} (if the data are spatitally extensive e.g.
-#'     population counts), \code{"intensive"} (if the data are spatially intensive e.g.
-#'     population density), or \code{"mixed"} (if the data include both extensive and
-#'     intensive values). If \code{"extensive"}, the sum is returned for the interpolated
-#'     value. If \code{"intensive"}, the mean is returned for the interpolated value.
-#'     If \code{"mixed"}, vectors named \code{"extensive"} and \code{"intensive"} containing
-#'     the relevant variable names should be specified in the dots.
 #' @param weight For \code{"extensive"} interpolations, should be either \code{"total"} or
-#'     \code{"sum"}. For \code{"intensive"} interpolations, should be \code{"sum"}.
+#'     \code{"sum"}. For \code{"intensive"} interpolations, should be \code{"sum"}. For mixed
+#'     interpolations, this will only impact the calculation of the extensive variables.
 #' @param output One of either \code{"sf"} or \code{"tibble"}
-#' @param ... If the \code{class} argument is \code{"extensive"} or \code{"intensive"},
-#'     this should be a list of columns from \code{source}, with each name quoted, that should
-#'     interpolated into the \code{target} data (these are referred to as the \code{value}
-#'     elsewhere in the package). If the \code{class} argument is \code{"mixed"}, this should
-#'     contain two vectors created using \code{c()} named \code{"extensive"} and \code{"intensive"}
-#'     containing the relevant variable names.
[…]

### 2018-12-14 inst/extdata/createData.R

@@ -51,3 +51,22 @@ use_data(aw_stl_wardsClipped, overwrite = TRUE)
 use_data(aw_stl_asthma, overwrite = TRUE)
 
 rm(stlRace, stlTracts, aw_stl_race, aw_stl_wards, aw_stl_asthma, aw_stl_wardsClipped)
+
+devtools::load_all()
+
+## create modified asthma data
+aw_stl_asthma %>%
+  dplyr::select(-STATEFP, -COUNTYFP, -TRACTCE, -NAMELSAD, -ALAND, -AWATER) %>%
+  dplyr::mutate(ASTHMA2 = ASTHMA/2) -> asthma
+
+## create combined data
+### remove sf geometry
+race <- aw_stl_race
+sf::st_geometry(race) <- NULL
+
+### create combined data
+race %>%
+  dplyr::select(GEOID, TOTAL_E, WHITE_E, BLACK_E) %>%
+  dplyr::left_join(asthma, ., by = "GEOID") -> combinedData
+
+usethis::use_data(combinedData, overwrite = TRUE)

### 2018-12-14 inst/extdata/functionTest.R

@@ -17,8 +17,8 @@ aw_interpolate(wards, tid = WARD, source = race2, sid = "GEOID", output = "tibbl
 
 wards %>%
   select(-OBJECTID, -AREA) %>%
-  aw_interpolate(tid = WARD, source = race, sid = "GEOID", type = "extensive", weight = "sum", output = "sf",
-                 "TOTAL_E", "WHITE_E", "BLACK_E")
+  aw_interpolate(tid = WARD, source = race, sid = "GEOID", weight = "sum", output = "sf",
+                 extensive = c("TOTAL_E", "WHITE_E", "BLACK_E"))
 
 aw_interpolate(wards, tid = WARD, source = race, sid = "GEOID", type = "extensive", output = "sf", "TOTAL_E")
 aw_interpolate(wards, tid = WARD, source = asthma, sid = "geoID", type = "intensive", output = "sf", "pctAsthma")

### 2018-12-14 tests/testthat/test_interpolate.R

@@ -2,33 +2,110 @@ context("test aw_interpolate function")
 
 # load test data ------------------------------------------------
 
+# target data
+data(aw_stl_wards, package = "areal")
+
 # source data
 data(aw_stl_race, package = "areal")
 data(aw_stl_asthma, package = "areal")
 
-# target data
-data(aw_stl_wards, package = "areal")
-
 # create comparison data
+load(system.file("extdata", "combinedData.rda", package = "areal", mustWork = TRUE))
 load(system.file("extdata", "totalCompare1.rda", package = "areal", mustWork = TRUE))
 totalCompare2 <- suppressWarnings(sf::st_interpolate_aw(aw_stl_race["TOTAL_E"], aw_stl_wards, extensive = TRUE))
 asthmaCompare <- suppressWarnings(sf::st_interpolate_aw(aw_stl_asthma["ASTHMA"], aw_stl_wards, extensive = FALSE))
 
 # test errors ------------------------------------------------
 
+test_that("errors with missing parameters", {
+  expect_error(aw_interpolate(aw_stl_wards, source = aw_stl_race, sid = GEOID,
+                              weight = "sum", output = "sf", extensive = "TOTAL_E"),
+               "A variable name must be specified for the 'tid' argument.")
+})
+
+test_that("errors with objects and id variables that do not exist", {
+  expect_error(aw_interpolate(ham, tid = WARD, source = aw_stl_race, sid = GEOID,
+                              weight = "sum", output = "sf", extensive = "TOTAL_E"),
+               "Object 'ham' not found.")
+  expect_error(aw_interpolate(aw_stl_wards, tid = WARD, source = ham, sid = GEOID,
+                              weight = "sum", output = "sf", extensive = "TOTAL_E"),
+               "Object 'ham' not found.")
+  expect_error(aw_interpolate(aw_stl_wards, tid = ham, source = aw_stl_race, sid = GEOID,
+                              weight = "sum", output = "sf", extensive = "TOTAL_E"),
+               "Variable 'ham', given for the target ID \\('tid'\\), cannot be found in the given target object.")
+  expect_error(aw_interpolate(aw_stl_wards, tid = "ham", source = aw_stl_race, sid = GEOID,
+                              weight = "sum", output = "sf", extensive = "TOTAL_E"),
[…]

### 2018-12-14 tests/testthat/test_interpolate.R
addressing issues with combinedData.rda

@@ -8,10 +8,10 @@ data(aw_stl_wards, package = "areal")
 # source data
 data(aw_stl_race, package = "areal")
 data(aw_stl_asthma, package = "areal")
+load(system.file("testdata", "combinedData.rda", package = "areal", mustWork = TRUE))
 
 # create comparison data
-load(system.file("extdata", "combinedData.rda", package = "areal", mustWork = TRUE))
-load(system.file("extdata", "totalCompare1.rda", package = "areal", mustWork = TRUE))
+load(system.file("testdata", "totalCompare1.rda", package = "areal", mustWork = TRUE))
 totalCompare2 <- suppressWarnings(sf::st_interpolate_aw(aw_stl_race["TOTAL_E"], aw_stl_wards, extensive = TRUE))
 asthmaCompare <- suppressWarnings(sf::st_interpolate_aw(aw_stl_asthma["ASTHMA"], aw_stl_wards, extensive = FALSE))
 
@@ -63,20 +63,6 @@ test_that("correctly specified functions execute without error", {
                               weight = "sum", output = "sf", intensive = "ASTHMA"), NA)
   expect_error(aw_interpolate(aw_stl_wards, tid = "WARD", source = aw_stl_asthma, sid = "GEOID",
                               weight = "sum", output = "sf", intensive = "ASTHMA"), NA)
-  expect_error(aw_interpolate(aw_stl_wards, tid = "WARD", source = aw_stl_asthma, sid = "GEOID",
-                              weight = "sum", output = "sf", intensive = c("ASTHMA", "ASTHMA2")), NA)
-  expect_error(aw_interpolate(aw_stl_wards, tid = WARD, source = combinedData, sid = GEOID,
-                              weight = "sum", output = "sf", extensive = "TOTAL_E",
-                              intensive = "ASTHMA"), NA)
-  expect_error(aw_interpolate(aw_stl_wards, tid = WARD, source = combinedData, sid = GEOID,
-                              weight = "total", output = "sf", extensive = "TOTAL_E",
-                              intensive = "ASTHMA"), NA)
-  expect_error(aw_interpolate(aw_stl_wards, tid = WARD, source = combinedData, sid = GEOID,
-                              weight = "sum", output = "sf", extensive = c("TOTAL_E", "WHITE_E", "BLACK_E"),
-                              intensive = c("ASTHMA", "ASTHMA2")), NA)
[…]

### 2018-12-14 README.Rmd
pull out combined tests, update README with api changes

@@
 ```{r iteration}
-aw_interpolate(wards, tid = WARD, source = race, sid = "GEOID", type = "extensive", 
-               weight = "sum", output = "tibble", "TOTAL_E", "WHITE_E", "BLACK_E")
+aw_interpolate(wards, tid = WARD, source = race, sid = "GEOID", weight = "sum", 
+               output = "tibble", extensive = c("TOTAL_E", "WHITE_E", "BLACK_E"))
 ```
@@
 ```{r intensive}
-aw_interpolate(wards, tid = WARD, source = asthma, sid = "GEOID", type = "intensive", 
-               weight = "sum", output = "tibble", "ASTHMA")
+aw_interpolate(wards, tid = WARD, source = asthma, sid = "GEOID", 
+               weight = "sum", output = "tibble", intensive = "ASTHMA")
 ```
@@
 # interpolate
-aw_interpolate(wards, tid = WARD, source = combinedData, sid = "GEOID", type = "mixed", 
+aw_interpolate(wards, tid = WARD, source = combinedData, sid = "GEOID",
                weight = "sum", output = "tibble", 
@@
 ```{r sf-output}
-aw_interpolate(wards, tid = "WARD", source = race, sid = "GEOID", type = "extensive", 
-               weight = "sum", output = "sf", "TOTAL_E", "WHITE_E", "BLACK_E")
+aw_interpolate(wards, tid = "WARD", source = race, sid = "GEOID",  
+               weight = "sum", output = "sf", 
+               extensive = c("TOTAL_E", "WHITE_E", "BLACK_E"))
 ```
@@
   select(-OBJECTID, -AREA) %>%
-  aw_interpolate(tid = WARD, source = race, sid = "GEOID", type = "extensive", 
-               weight = "sum", output = "tibble", "TOTAL_E", "WHITE_E", "BLACK_E")
+  aw_interpolate(tid = WARD, source = race, sid = "GEOID", 
+               weight = "sum", output = "tibble", 
+               extensive = c("TOTAL_E", "WHITE_E", "BLACK_E"))
 ```

### 2018-12-14 inst/extdata/createData.R

@@ -51,22 +51,3 @@ use_data(aw_stl_wardsClipped, overwrite = TRUE)
 use_data(aw_stl_asthma, overwrite = TRUE)
 
 rm(stlRace, stlTracts, aw_stl_race, aw_stl_wards, aw_stl_asthma, aw_stl_wardsClipped)
-
-devtools::load_all()
-
-## create modified asthma data
-aw_stl_asthma %>%
-  dplyr::select(-STATEFP, -COUNTYFP, -TRACTCE, -NAMELSAD, -ALAND, -AWATER) %>%
-  dplyr::mutate(ASTHMA2 = ASTHMA/2) -> asthma
-
-## create combined data
-### remove sf geometry
-race <- aw_stl_race
-sf::st_geometry(race) <- NULL
-
-### create combined data
-race %>%
-  dplyr::select(GEOID, TOTAL_E, WHITE_E, BLACK_E) %>%
-  dplyr::left_join(asthma, ., by = "GEOID") -> combinedData
-
-usethis::use_data(combinedData, overwrite = TRUE)

### 2018-12-14 inst/testdata/combinedData.R

@@ -1,0 +1,20 @@
+# create combined data
+
+devtools::load_all()
+
+## create modified asthma data
+aw_stl_asthma %>%
+  dplyr::select(-STATEFP, -COUNTYFP, -TRACTCE, -NAMELSAD, -ALAND, -AWATER) %>%
+  dplyr::mutate(ASTHMA2 = ASTHMA/2) -> asthma
+
+## create combined data
+### remove sf geometry
+race <- aw_stl_race
+sf::st_geometry(race) <- NULL
+
+### create combined data
+race %>%
+  dplyr::select(GEOID, TOTAL_E, WHITE_E, BLACK_E) %>%
+  dplyr::left_join(asthma, ., by = "GEOID") -> combinedData
+
+usethis::use_data(combinedData, overwrite = TRUE)

### 2018-12-14 tests/testthat/test_interpolate.R

@@ -76,22 +76,15 @@ totalResult2 <- aw_interpolate(aw_stl_wards, tid = WARD, source = aw_stl_race, s
 asthmaResult <- aw_interpolate(aw_stl_wards, tid = WARD, source = aw_stl_asthma, sid = GEOID,
                                output = "sf", weight = "sum", intensive = "ASTHMA")
 
-mixedResult <- aw_interpolate(aw_stl_wards, tid = WARD, source = combinedData, sid = "GEOID",
-                              weight = "sum", output = "tibble", extensive = "TOTAL_E",
-                              intensive = "ASTHMA")
-
 test_that("interpolated values are equal", {
   expect_equal(totalCompare1$TOTAL_E, totalResult1$TOTAL_E)
   expect_equal(totalCompare2$TOTAL_E, totalResult2$TOTAL_E)
   expect_equal(asthmaCompare$ASTHMA, asthmaResult$ASTHMA)
-  expect_equal(totalCompare1$TOTAL_E, mixedResult$TOTAL_E)
-  expect_equal(asthmaCompare$ASTHMA, mixedResult$ASTHMA)
 })
 
 test_that("classes are created appropriately", {
   expect_equal("sf", class(totalResult1)[1])
   expect_equal("sf", class(totalResult2)[1])
   expect_equal("sf", class(asthmaResult)[1])
-  expect_equal("tbl_df", class(mixedResult)[1])
 })
 

### 2018-12-14 README.Rmd
short sf example

@@
 aw_interpolate(wards, tid = "WARD", source = race, sid = "GEOID",  
-               weight = "sum", output = "sf", 
-               extensive = c("TOTAL_E", "WHITE_E", "BLACK_E"))
+               weight = "sum", output = "sf", extensive = "TOTAL_E")
 ```

### 2018-12-14 README.Rmd
updates to README intro

@@
 
-`areal` offers an intuitive assortment of options to validate, interpolate, and compare fields between a source and target data set.
-While methods for implementing areal weighted interpolation are available outside of the `R` ecosystem (ex - toolboxes in ArcGIS) and within `R` (the `sf` package's `st_interpolate_aw`) function, `areal` fills a niche by providing additional functionality not available in `sf` while taking advantage of the reproducibility of `R`.
-
+`areal` offers an intuitive toolkit for validating and interpolating spatial data.
+Areal interpolations is the process making estimates about the population features from a source set of polygons to an overlapping but incongruent set of target polygons - is the lack of easy to use tools for completing the processes.
+While methods for implementing various areal interpolation approaches are available outside of the `R` ecosystem (ex - toolboxes in ArcGIS) and within `R` (the `sf` package's `st_interpolate_aw`) function, `areal` fills a niche by providing additional functionality not available in `sf` while taking advantage of the reproducibility of `R`.
 `areal` currently implents only areal weighted interpolation, but a roadmap is being developed to add additional interpolation methods as well.

### 2018-12-17 R/aw_verify.R
finish logic checks for aw_verify

@@ -61,12 +61,8 @@ aw_verify <- function(source, sourceValue, result, resultValue){
                     var = sourceValueQN))
   }
 
-  if (length(resultValueQN) > 1){
-    stop("The 'resultVar' parameter should have only one variable name given.")
-  }
-
   if(!!resultValueQN %in% colnames(result) == FALSE) {
-    stop(glue::glue("Variable '{var}', given for the result value, cannot be found in the given result object.",
+    stop(glue::glue("Variable '{var}', given for the result value, cannot be found in the given result object. Make sure only one existing variable is given.",
                     var = resultValueQN))
   }
 

### 2018-12-17 tests/testthat/test_aw_verify.R

@@ -9,31 +9,46 @@ data(aw_stl_wards, package = "areal")
 data(aw_stl_race, package = "areal")
 
 # interpolate data
-totalResult <- aw_interpolate(aw_stl_wards, tid = WARD, source = aw_stl_race, sid = GEOID,
+totalResult1 <- aw_interpolate(aw_stl_wards, tid = WARD, source = aw_stl_race, sid = GEOID,
                                weight = "sum", output = "sf", extensive = "TOTAL_E")
+
+totalResult2 <- aw_interpolate(aw_stl_wards, tid = WARD, source = aw_stl_race, sid = GEOID,
+                              weight = "total", output = "sf", extensive = "TOTAL_E")
 
 # test errors ------------------------------------------------
 
 test_that("errors with missing objects", {
-  expect_error(aw_verify(source = ham, sourceValue = TOTAL_E, result = totalResult, resultValue = TOTAL_E),
+  expect_error(aw_verify(source = ham, sourceValue = TOTAL_E, result = totalResult1, resultValue = TOTAL_E),
                "object 'ham' not found")
   expect_error(aw_verify(source = aw_stl_race, sourceValue = TOTAL_E, result = ham, resultValue = TOTAL_E),
                "object 'ham' not found")
 })
 
 test_that("errors with missing parameters", {
-  expect_error(aw_verify(sourceValue = TOTAL_E, result = totalResult, resultValue = TOTAL_E),
+  expect_error(aw_verify(sourceValue = TOTAL_E, result = totalResult1, resultValue = TOTAL_E),
                "A sf object containing source data must be specified for the 'source' argument.")
-  expect_error(aw_verify(source = aw_stl_race, result = totalResult, resultValue = TOTAL_E),
+  expect_error(aw_verify(source = aw_stl_race, result = totalResult1, resultValue = TOTAL_E),
                "A variable name must be specified for the 'sourceValue' argument.")
   expect_error(aw_verify(source = aw_stl_race, sourceValue = TOTAL_E, resultValue = TOTAL_E),
                "A sf object containing interpolated data must be specified for the 'result' argument.")
-  expect_error(aw_verify(source = aw_stl_race, sourceValue = TOTAL_E, result = totalResult),
+  expect_error(aw_verify(source = aw_stl_race, sourceValue = TOTAL_E, result = totalResult1),
                "A variable name must be specified for the 'resultValue' argument.")
 })
 
 test_that("errors with misspecified parameters", {
[…]

### 2018-12-17 README.Rmd
start working on areal vignette

@@
 `areal` offers an intuitive toolkit for validating and interpolating spatial data.
-Areal interpolations is the process making estimates about the population features from a source set of polygons to an overlapping but incongruent set of target polygons - is the lack of easy to use tools for completing the processes.
+Areal interpolation is the process making estimates about the population features from a source set of polygons to an overlapping but incongruent set of target polygons - is the lack of easy to use tools for completing the processes.
 While methods for implementing various areal interpolation approaches are available outside of the `R` ecosystem (ex - toolboxes in ArcGIS) and within `R` (the `sf` package's `st_interpolate_aw`) function, `areal` fills a niche by providing additional functionality not available in `sf` while taking advantage of the reproducibility of `R`.

### 2018-12-17 README.Rmd
update README and create index.Rmd for pkgdown site

--- 2018-12-14 README.Rmd
@@
 
-`areal` offers an intuitive assortment of options to validate, interpolate, and compare fields between a source and target data set.
-While methods for implementing areal weighted interpolation are available outside of the `R` ecosystem (ex - toolboxes in ArcGIS) and within `R` (the `sf` package's `st_interpolate_aw`) function, `areal` fills a niche by providing additional functionality not available in `sf` while taking advantage of the reproducibility of `R`.
-
-`areal` currently implents only areal weighted interpolation, but a roadmap is being developed to add additional interpolation methods as well.
-This will be posted on the package's website before the initial CRAN release.
+Areal interpolation is the process making estimates about the population features from a source set of polygons to an overlapping but incongruent set of target polygons.
+One challenge with areal interpolation is that, while the processes themselves are well documented, implementing them often involves "reinventing the wheel." Within `R`, the `sf` package does offer a basic interface for areal weighted interpolation (`st_interpolate_aw`).
+The `areal` package is designed to provide a suite of interpolation functions that provide a more full-featured workflow that fits into both modern data management (e.g.
+`tidyverse`) and spatial data (e.g.
+`sf`) frameworks.
 
@@
 ### Installing Dependencies
-
 You should check the [`sf` package website](https://r-spatial.github.io/sf/) for the latest details on installing dependencies for that package.
@@
 ## Usage 
-The package contains three overlapping data sets:
+### Data
+The package contains four overlapping data sets:
 
@@
 * `aw_stl_wards` (the 2010 political subdivisions in St. Louis; *n* = 28). 
+* `aw_stl_wardsClipped` (the 2010 political subdivisions in St. Louis clipped to the Mississippi River shoreline; *n* = 28).
 
-These can be used to illustrate the core functionality of the package.
-
-The basic usage of `areal` is through the `aw_interpolate()` function, which is illustrated below. The following examples assume:
+These can be used to illustrate the core functionality of the package. The following examples assume:
 
@@
 
-### Data Validation
-`areal` contains a detailed data validation workflow that ensures that both the `source` and `target` data are compatible with each either. It can be run in a simple format:
+### Areal Weighted Interpolation
+`areal` currently implements an approach to interpolation known as areal weighted interpolation.
+It is arguably the simplest and most common approach to areal interpolation, though it does have some drawbacks (see the [areal weighted interpolation vignette](https://slu-opengis.github.io/areal/articles/areal-weighted-interpolation.html) for details).
+The basic usage of `areal` is through the `aw_interpolate()` function.
+This is a pipe-able function that allows for the simultaneous interpolation of multiple values.
 
-```{r validate-simple}
-aw_validate(source = asthma, target = wards, varList = c("ASTHMA"))
+In this first example, the total estimated population (`TOTAL_E`) of each ward is calculated from its overlapping census tracts:
+
+```{r iteration}
+aw_interpolate(wards, tid = WARD, source = race, sid = "GEOID", 
+               weight = "sum", output = "sf", extensive = "TOTAL_E")
 ```
 
-If `aw_validate()` returns a `FALSE` value, it can also be run in a verbose manner that returns a detailed tibble:
+This example outputs a simple features (`sf`) object and uses one of two options for calculating weights.
+All of these arguments are documented both within the package (use `?aw_interpolate`) and on the [package's website](https://slu-opengis.github.io/areal/).
 
-```{r validate-verbose}
-aw_validate(source = asthma, target = wards, varList = c("ASTHMA"), verbose = TRUE)
-```
-
-### Built-in Iteration
-
-One advantage of `areal` is that it allows for multiple values to be interpolated at a time.
-Here, both total estiatmed population (`TOTAL_E`), the estimated count of white residents (`WHITE_E`), and the estimated count of African American residents (`BLACK_E`) are interpolated at once:
-
-```{r iteration}
-aw_interpolate(wards, tid = WARD, source = race, sid = "GEOID", weight = "sum", 
-               output = "tibble", extensive = c("TOTAL_E", "WHITE_E", "BLACK_E"))
-```
-
-### Interpolation Choices
-Both spatially extensive (i.e.
-counts; illustrated in the prior examples) and spatially intensive (i.e.
-ratios) data can be interpolated.
-For spatially intensive data, the average is returned rather than the sum:
-
-```{r intensive}
-aw_interpolate(wards, tid = WARD, source = asthma, sid = "GEOID", 
-               weight = "sum", output = "tibble", intensive = "ASTHMA")
-```
-
-Both extensive and intensive data can be interpolated simultaneously by setting `type` to `"mixed"` and naming two vectors `extensive` and `intensive`.
-These vectors should include the relevent variable names:
+Both extensive and intensive data can be interpolated simultaneously by using both the `extensive` and `intensive` arguments.
+In this second example, the asthma and race data are combined, and estimates for both the population values and asthma rates are calculated for each ward from its overlapping census tracts:
 
@@
 # remove sf geometry
-raceTable <- race
-st_geometry(raceTable) <- NULL
+st_geometry(race) <- NULL
 
 # create combined data
-raceTable %>%
+race %>%
   select(GEOID, TOTAL_E, WHITE_E, BLACK_E) %>%
@@
 # interpolate
-aw_interpolate(wards, tid = WARD, source = combinedData, sid = "GEOID",
-               weight = "sum", output = "tibble", 
+wards %>%
+  select(-OBJECTID, -AREA) %>%
+  aw_interpolate(tid = WARD, source = combinedData, sid = "GEOID", 
+               weight = "total", output = "tibble", 
                extensive = c("TOTAL_E", "WHITE_E", "BLACK_E"),
-               intensive = c("ASTHMA"))
+               intensive = "ASTHMA")
 ```
 
-### Output Choices
-Output can be either a tibble (shown in the prior example) or an `sf` object:
+Another advantage of `areal` is that the interpolation process is not a "black box", but rather can be manually completed if necessary.
+Functions for validating data, previewing the areal weights, and walking step-by-step through the interpolation process are provided.
+See the [areal weighted interpolation vignette](https://slu-opengis.github.io/areal/articles/areal-weighted-interpolation.html) for additional details about this workflow.
 
-```{r sf-output}
-aw_interpolate(wards, tid = "WARD", source = race, sid = "GEOID",  
-               weight = "sum", output = "sf", extensive = "TOTAL_E")
-```
+## Road-map 
+We are planning to experiment with at least three additional techniques for areal interpolation for possible inclusion into the package. These include:
 
-### Pipe Compatible
+- [Pycnophylactic method](https://github.com/slu-openGIS/areal/issues/1) (raster based, eliminates the sharp transitions in value between target features)
+- [Binary dasymetric method](https://github.com/slu-openGIS/areal/issues/2) (incorporates ancillary data so that population is not assumed to be evenly distributed within units)
+- [3-class regression dasymetric method](https://github.com/slu-openGIS/areal/issues/3) (allows for a more complex estimation based on multiple forms of ancillary data)
 
-One key advantage of `areal` is that is pipeable, meaning that it can fit easily into existing `tidyverse` workflows:
+We do not have a timeline for these experiments, though we are planning to begin experimenting with the pycnophylactic method in the coming months.
+We will be keeping the issues (linked to above) updated with progress.
+If you are interested in bringing these techniques to `R`, please feel free to contribute to the development of `areal`.
+The best place to start is bt checking in on our GitHub issues for each technique to see what help is needed!
 
-```{r pipe}
-wards %>%
-  select(-OBJECTID, -AREA) %>%
-  aw_interpolate(tid = WARD, source = race, sid = "GEOID", 
-               weight = "sum", output = "tibble", 
-               extensive = c("TOTAL_E", "WHITE_E", "BLACK_E"))
-```
-
-### Transparent
-
-Another advantage of `areal` is that the interpolation process is not a "black box", but rather can be manually completed if necessary. Details on this will be available on the package's website.
+## Contributor Code of Conduct
+Please note that this project is released with a [Contributor Code of Conduct](.github/CODE_OF_CONDUCT.md). By participating in this project you agree to abide by its terms.

### 2018-12-17 index.Rmd
update README and create index.Rmd for pkgdown site

--- 2018-12-17 README.Rmd
@@
   comment = "#>",
-  fig.path = "man/figures/README-",
+  fig.path = "man/figures/index-",
   out.width = "100%"
 )
-
-library(areal)
-library(dplyr)
-library(sf)
-
-data(aw_stl_asthma, package = "areal")
-asthma <- aw_stl_asthma
-
-data(aw_stl_race, package = "areal")
-race <- aw_stl_race
-
-data(aw_stl_wards, package = "areal")
-wards <- aw_stl_wards
 ```
@@
 
-## Usage 
-### Data
-The package contains four overlapping data sets:
-
-* `aw_stl_race` (2017 ACS demographic counts at the census tract level; *n* = 106) 
-* `aw_stl_asthma` (2017 asthma rates at the census tract level; *n* = 106)
-* `aw_stl_wards` (the 2010 political subdivisions in St. Louis; *n* = 28). 
-* `aw_stl_wardsClipped` (the 2010 political subdivisions in St. Louis clipped to the Mississippi River shoreline; *n* = 28).
-
-These can be used to illustrate the core functionality of the package. The following examples assume:
-
-```r
-> library(areal)
->
-> race <- aw_stl_race
-> asthma <- aw_stl_asthma
-> wards <- aw_stl_wards
-```
-
-### Areal Weighted Interpolation
-`areal` currently implements an approach to interpolation known as areal weighted interpolation.
-It is arguably the simplest and most common approach to areal interpolation, though it does have some drawbacks (see the [areal weighted interpolation vignette](https://slu-opengis.github.io/areal/articles/areal-weighted-interpolation.html) for details).
-The basic usage of `areal` is through the `aw_interpolate()` function.
-This is a pipe-able function that allows for the simultaneous interpolation of multiple values.
-
-In this first example, the total estimated population (`TOTAL_E`) of each ward is calculated from its overlapping census tracts:
-
-```{r iteration}
-aw_interpolate(wards, tid = WARD, source = race, sid = "GEOID", 
-               weight = "sum", output = "sf", extensive = "TOTAL_E")
-```
-
-This example outputs a simple features (`sf`) object and uses one of two options for calculating weights.
-All of these arguments are documented both within the package (use `?aw_interpolate`) and on the [package's website](https://slu-opengis.github.io/areal/).
-
-Both extensive and intensive data can be interpolated simultaneously by using both the `extensive` and `intensive` arguments.
-In this second example, the asthma and race data are combined, and estimates for both the population values and asthma rates are calculated for each ward from its overlapping census tracts:
-
-```{r mixed}
-# remove sf geometry
-st_geometry(race) <- NULL
-
-# create combined data
-race %>%
-  select(GEOID, TOTAL_E, WHITE_E, BLACK_E) %>%
-  left_join(asthma, ., by = "GEOID") -> combinedData
-
-# interpolate
-wards %>%
-  select(-OBJECTID, -AREA) %>%
-  aw_interpolate(tid = WARD, source = combinedData, sid = "GEOID", 
-               weight = "total", output = "tibble", 
-               extensive = c("TOTAL_E", "WHITE_E", "BLACK_E"),
-               intensive = "ASTHMA")
-```
-
-Another advantage of `areal` is that the interpolation process is not a "black box", but rather can be manually completed if necessary.
-Functions for validating data, previewing the areal weights, and walking step-by-step through the interpolation process are provided.
-See the [areal weighted interpolation vignette](https://slu-opengis.github.io/areal/articles/areal-weighted-interpolation.html) for additional details about this workflow.
-
-## Road-map 
-We are planning to experiment with at least three additional techniques for areal interpolation for possible inclusion into the package. These include:
-
-- [Pycnophylactic method](https://github.com/slu-openGIS/areal/issues/1) (raster based, eliminates the sharp transitions in value between target features)
-- [Binary dasymetric method](https://github.com/slu-openGIS/areal/issues/2) (incorporates ancillary data so that population is not assumed to be evenly distributed within units)
-- [3-class regression dasymetric method](https://github.com/slu-openGIS/areal/issues/3) (allows for a more complex estimation based on multiple forms of ancillary data)
-
-We do not have a timeline for these experiments, though we are planning to begin experimenting with the pycnophylactic method in the coming months.
-We will be keeping the issues (linked to above) updated with progress.
-If you are interested in bringing these techniques to `R`, please feel free to contribute to the development of `areal`.
-The best place to start is bt checking in on our GitHub issues for each technique to see what help is needed!
-
 ## Contributor Code of Conduct

### 2018-12-17 README.Rmd
update installation instructions

@@
 Instructions vary significantly by operating system.
-For best results, have `sf` installed before you install `qualmap`.
+For best results, have `sf` installed before you install `areal`.
 Other dependencies, like `dplyr`, will be installed automatically with `areal` if they are not already present.
+
+The one exception here is the dependency `lwgeom`, which Linux users will need to follow some [spatial instructions](https://github.com/r-spatial/lwgeom) to install correctly.
 

### 2018-12-17 R/aw_verify.R
clarify aw_verify docs

@@ -1,7 +1,9 @@
-#' Verify Correct Interpolation
+#' Verify Correct Extensive-Sum Interpolation
 #'
 #' @details \code{aw_verify} ensures that the sum of the resulting interpolated
-#'     value is equal to the sum of the origina source value.
+#'     value is equal to the sum of the origina source value. This functionality
+#'     only works for interpolations that are extensive and use the \code{sum}
+#'     approach to calculating areal weights.
 #'
 #' @usage aw_verify(source, sourceValue, result, resultValue)
 #'

### 2018-12-17 README.Rmd
small changes preparing for initial pre-CRAN release

@@
 One challenge with areal interpolation is that, while the processes themselves are well documented, implementing them often involves "reinventing the wheel." Within `R`, the `sf` package does offer a basic interface for areal weighted interpolation (`st_interpolate_aw`).
-The `areal` package is designed to provide a suite of interpolation functions that provide a more full-featured workflow that fits into both modern data management (e.g.
+The `areal` package contains a suite tools for validation and estimation, providing a full-featured workflow that fits into both modern data management (e.g.
 `tidyverse`) and spatial data (e.g.

### 2018-12-17 README.Rmd
rename data objects

@@
 
-data(aw_stl_asthma, package = "areal")
+data(ar_stl_asthma, package = "areal")
 asthma <- aw_stl_asthma
 
-data(aw_stl_race, package = "areal")
+data(ar_stl_race, package = "areal")
 race <- aw_stl_race
 
-data(aw_stl_wards, package = "areal")
+data(ar_stl_wards, package = "areal")
 wards <- aw_stl_wards
@@
 
-* `aw_stl_race` (2017 ACS demographic counts at the census tract level; *n* = 106) 
-* `aw_stl_asthma` (2017 asthma rates at the census tract level; *n* = 106)
-* `aw_stl_wards` (the 2010 political subdivisions in St. Louis; *n* = 28). 
-* `aw_stl_wardsClipped` (the 2010 political subdivisions in St. Louis clipped to the Mississippi River shoreline; *n* = 28).
+* `ar_stl_race` (2017 ACS demographic counts at the census tract level; *n* = 106) 
+* `ar_stl_asthma` (2017 asthma rates at the census tract level; *n* = 106)
+* `ar_stl_wards` (the 2010 political subdivisions in St. Louis; *n* = 28). 
+* `ar_stl_wardsClipped` (the 2010 political subdivisions in St. Louis clipped to the Mississippi River shoreline; *n* = 28).
 

### 2018-12-17 R/ar_stl_asthma.R

@@ -5,7 +5,7 @@
 #'
 #' @docType data
 #'
-#' @usage data(aw_stl_asthma)
+#' @usage data(ar_stl_asthma)
 #'
 #' @format A data frame with 106 rows and 24 variables:
 #' \describe{
@@ -23,8 +23,8 @@
 #' @source Centers for Disease Control's 500 Cities Data
 #'
 #' @examples
-#' str(aw_stl_asthma)
-#' head(aw_stl_asthma)
-#' summary(aw_stl_asthma$ASTHMA)
+#' str(ar_stl_asthma)
+#' head(ar_stl_asthma)
+#' summary(ar_stl_asthma$ASTHMA)
 #'
-"aw_stl_asthma"
+"ar_stl_asthma"

### 2018-12-17 R/ar_stl_race.R

@@ -5,7 +5,7 @@
 #'
 #' @docType data
 #'
-#' @usage data(aw_stl_race)
+#' @usage data(ar_stl_race)
 #'
 #' @format A data frame with 106 rows and 24 variables:
 #' \describe{
@@ -38,8 +38,8 @@
 #' @source \code{tidycensus} package
 #'
 #' @examples
-#' str(aw_stl_race)
-#' head(aw_stl_race)
-#' summary(aw_stl_race$ALAND)
+#' str(ar_stl_race)
+#' head(ar_stl_race)
+#' summary(ar_stl_race$ALAND)
 #'
-"aw_stl_race"
+"ar_stl_race"

### 2018-12-17 R/ar_stl_wards.R

@@ -7,7 +7,7 @@
 #'
 #' @docType data
 #'
-#' @usage data(aw_stl_wards)
+#' @usage data(ar_stl_wards)
 #'
 #' @format A data frame with 28 rows and 4 variables:
 #' \describe{
@@ -20,8 +20,8 @@
 #' @source City of St. Louis
 #'
 #' @examples
-#' str(aw_stl_wards)
-#' head(aw_stl_wards)
-#' summary(aw_stl_wards$AREA)
+#' str(ar_stl_wards)
+#' head(ar_stl_wards)
+#' summary(ar_stl_wards$AREA)
 #'
-"aw_stl_wards"
+"ar_stl_wards"

### 2018-12-17 R/ar_stl_wardsClipped.R

@@ -7,7 +7,7 @@
 #'
 #' @docType data
 #'
-#' @usage data(aw_stl_wardsClipped)
+#' @usage data(ar_stl_wardsClipped)
 #'
 #' @format A data frame with 28 rows and 2 variables:
 #' \describe{
@@ -18,7 +18,7 @@
 #' @source City of St. Louis
 #'
 #' @examples
-#' str(aw_stl_wardsClipped)
-#' head(aw_stl_wardsClipped)
+#' str(ar_stl_wardsClipped)
+#' head(ar_stl_wardsClipped)
 #'
-"aw_stl_wardsClipped"
+"ar_stl_wardsClipped"

### 2018-12-17 inst/extdata/createData.R

@@ -23,31 +23,27 @@ tracts(state = 29, county = 510, class = "sf") %>%
   select(GEOID, STATEFP, COUNTYFP, TRACTCE, NAMELSAD, ALAND, AWATER) -> stlTracts
 
 left_join(stlTracts, stlRace, by = "GEOID") %>%
-  st_transform(crs = 26915) -> aw_stl_race
+  st_transform(crs = 26915) -> ar_stl_race
 
 st_read("inst/extdata/STL_POLITICS_Wards10.shp", stringsAsFactors = FALSE) %>%
   select(-Shape_Leng) %>%
   rename(AREA = Shape_Area,
          WARD = WARD10) %>%
-  st_transform(crs = 26915) -> aw_stl_wards
+  st_transform(crs = 26915) -> ar_stl_wards
 
 stl_tbl_asthma %>%
   rename(GEOID = geoID, ASTHMA = pctAsthma) %>%
   select(GEOID, ASTHMA) %>%
   left_join(aw_stl_race, ., by = "GEOID") %>%
-  select(GEOID, STATEFP, COUNTYFP, TRACTCE, NAMELSAD, ALAND, AWATER, ASTHMA) -> aw_stl_asthma
+  select(GEOID, STATEFP, COUNTYFP, TRACTCE, NAMELSAD, ALAND, AWATER, ASTHMA) -> ar_stl_asthma
 
 st_read("inst/extdata/STL_POLITICS_WardsClipped.shp", stringsAsFactors = FALSE) %>%
   select(-OBJECTID) %>%
-  st_transform(crs = 26915) -> aw_stl_wardsClipped
+  st_transform(crs = 26915) -> ar_stl_wardsClipped
 
-aw_stl_wards %>%
-  select(-AREA) %>%
-  st_write(.,"inst/stlWards.shp", delete_dsn = TRUE)
+use_data(ar_stl_race, overwrite = TRUE)
+use_data(ar_stl_wards, overwrite = TRUE)
+use_data(ar_stl_wardsClipped, overwrite = TRUE)
+use_data(ar_stl_asthma, overwrite = TRUE)
 
-use_data(aw_stl_race, overwrite = TRUE)
-use_data(aw_stl_wards, overwrite = TRUE)
-use_data(aw_stl_wardsClipped, overwrite = TRUE)
-use_data(aw_stl_asthma, overwrite = TRUE)
-
[…]

### 2018-12-17 inst/extdata/functionTest.R

@@ -1,47 +1,0 @@
-# test functions
-
-library(sf)
-library(dplyr)
-library(stldata)
-
-devtools::load_all()
-
-asthma <- stl_as_sf(stl_tbl_asthma)
-asthma <- st_transform(asthma, crs = 26915)
-race <- aw_stl_race
-wards <- aw_stl_wards
-
-aw_interpolate(ham, tid = WARD, source = race, sid = "GEOID", output = "tibble", "TOTAL_E", "WARD")
-
-aw_interpolate(wards, tid = WARD, source = race2, sid = "GEOID", output = "tibble", "TOTAL_E", "WARD")
-
-wards %>%
-  select(-OBJECTID, -AREA) %>%
-  aw_interpolate(tid = WARD, source = race, sid = "GEOID", weight = "sum", output = "sf",
-                 extensive = c("TOTAL_E", "WHITE_E", "BLACK_E"))
-
-aw_interpolate(wards, tid = WARD, source = race, sid = "GEOID", type = "extensive", output = "sf", "TOTAL_E")
-aw_interpolate(wards, tid = WARD, source = asthma, sid = "geoID", type = "intensive", output = "sf", "pctAsthma")
-
-asthma %>%
-  rename(GEOID = geoID) %>%
-  select(GEOID, pctAsthma) -> asthmaLite
-
-st_geometry(asthmaLite) <- NULL
-
-stl <- left_join(race, asthmaLite, by = "GEOID")
-
-wards %>%
-  select(-OBJECTID, -AREA) %>%
-  aw_interpolate(tid = WARD, source = stl, sid = "GEOID", type = "mixed", output = "sf",
-               extensive = "TOTAL_E", intensive = "pctAsthma")
-
-wards %>%
-  select(-OBJECTID, -AREA) %>%
-  aw_interpolate(tid = WARD, source = stl, sid = "GEOID", type = "mixed", output = "sf",
-                 extensive = c("TOTAL_E", "BLACK_E"), intensive = "pctAsthma")
-
-
-wards %>%
-  aw_intersect(source = race, areaVar = area) -> pkg
-

### 2018-12-17 README.Rmd
remove references to aw_ data

@@
 data(ar_stl_asthma, package = "areal")
-asthma <- aw_stl_asthma
+asthma <- ar_stl_asthma
 
 data(ar_stl_race, package = "areal")
-race <- aw_stl_race
+race <- ar_stl_race
 
 data(ar_stl_wards, package = "areal")
-wards <- aw_stl_wards
+wards <- ar_stl_wards
 ```

### 2018-12-17 tests/testthat/test_aw_aggregate.R

@@ -3,15 +3,15 @@ context("test aw_aggregate function")
 # load test data ------------------------------------------------
 
 # target data
-data(aw_stl_wards, package = "areal")
+data(ar_stl_wards, package = "areal")
 
 # source data
-data(aw_stl_race, package = "areal")
+data(ar_stl_race, package = "areal")
 
 # calculate intersection
-aw_stl_wards %>%
-  aw_intersect(source = aw_stl_race, areaVar = "...area") %>%
-  aw_total(source = aw_stl_race, id = GEOID, areaVar = "...area",
+ar_stl_wards %>%
+  aw_intersect(source = ar_stl_race, areaVar = "...area") %>%
+  aw_total(source = ar_stl_race, id = GEOID, areaVar = "...area",
            totalVar = "...totalArea", weight = "sum", type = "extensive") %>%
   aw_weight(areaVar = "...area", totalVar = "...totalArea", areaWeight = "...areaWeight") %>%
   aw_calculate(value = "TOTAL_E", areaWeight = "...areaWeight") -> intersect
@@ -19,33 +19,33 @@ aw_stl_wards %>%
 # test errors ------------------------------------------------
 
 test_that("errors with missing objects", {
-  expect_error(aw_aggregate(ham, target = aw_stl_wards, tid = WARD, interVar = "TOTAL_E"),
+  expect_error(aw_aggregate(ham, target = ar_stl_wards, tid = WARD, interVar = "TOTAL_E"),
                "object 'ham' not found")
   expect_error(aw_aggregate(intersect, target = ham, tid = WARD, interVar = "TOTAL_E"),
                "object 'ham' not found")
 })
 
 test_that("errors with missing parameters", {
-  expect_error(aw_aggregate(target = aw_stl_wards, tid = WARD, interVar = "TOTAL_E"),
+  expect_error(aw_aggregate(target = ar_stl_wards, tid = WARD, interVar = "TOTAL_E"),
                "A sf object containing intersected data must be specified for the '.data' argument.")
   expect_error(aw_aggregate(intersect, tid = WARD, interVar = "TOTAL_E"),
                "A sf object must be specified for the 'target' argument.")
-  expect_error(aw_aggregate(intersect, target = aw_stl_wards, interVar = "TOTAL_E"),
+  expect_error(aw_aggregate(intersect, target = ar_stl_wards, interVar = "TOTAL_E"),
[…]

### 2018-12-17 tests/testthat/test_aw_calculate.R

@@ -3,15 +3,15 @@ context("test aw_calculate function")
 # load test data ------------------------------------------------
 
 # target data
-data(aw_stl_wards, package = "areal")
+data(ar_stl_wards, package = "areal")
 
 # source data
-data(aw_stl_race, package = "areal")
+data(ar_stl_race, package = "areal")
 
 # calculate intersection
-aw_stl_wards %>%
-  aw_intersect(source = aw_stl_race, areaVar = "...area") %>%
-  aw_total(source = aw_stl_race, id = GEOID, areaVar = "...area",
+ar_stl_wards %>%
+  aw_intersect(source = ar_stl_race, areaVar = "...area") %>%
+  aw_total(source = ar_stl_race, id = GEOID, areaVar = "...area",
            totalVar = "...totalArea", weight = "sum", type = "extensive") %>%
   aw_weight(areaVar = "...area", totalVar = "...totalArea", areaWeight = "...areaWeight") -> intersect
 

### 2018-12-17 tests/testthat/test_aw_interpolate.R

@@ -3,20 +3,20 @@ context("test aw_interpolate function")
 # load test data ------------------------------------------------
 
 # target data
-data(aw_stl_wards, package = "areal")
+data(ar_stl_wards, package = "areal")
 
 # source data
-data(aw_stl_race, package = "areal")
-data(aw_stl_asthma, package = "areal")
+data(ar_stl_race, package = "areal")
+data(ar_stl_asthma, package = "areal")
 
 ## create modified asthma data
-aw_stl_asthma %>%
+ar_stl_asthma %>%
   dplyr::select(-STATEFP, -COUNTYFP, -TRACTCE, -NAMELSAD, -ALAND, -AWATER) %>%
   dplyr::mutate(ASTHMA2 = ASTHMA/2) -> asthma
 
 ## create combined data
 ### remove sf geometry
-race <- aw_stl_race
+race <- ar_stl_race
 sf::st_geometry(race) <- NULL
 
 ### create combined data
@@ -26,90 +26,90 @@ race %>%
 
 # create comparison data
 load(system.file("testdata", "totalCompare1.rda", package = "areal", mustWork = TRUE))
-totalCompare2 <- suppressWarnings(sf::st_interpolate_aw(aw_stl_race["TOTAL_E"], aw_stl_wards, extensive = TRUE))
-asthmaCompare <- suppressWarnings(sf::st_interpolate_aw(aw_stl_asthma["ASTHMA"], aw_stl_wards, extensive = FALSE))
+totalCompare2 <- suppressWarnings(sf::st_interpolate_aw(ar_stl_race["TOTAL_E"], ar_stl_wards, extensive = TRUE))
+asthmaCompare <- suppressWarnings(sf::st_interpolate_aw(ar_stl_asthma["ASTHMA"], ar_stl_wards, extensive = FALSE))
 
 # test errors ------------------------------------------------
 
 test_that("errors with missing objects", {
-  expect_error(aw_interpolate(ham, tid = WARD, source = aw_stl_race, sid = GEOID,
+  expect_error(aw_interpolate(ham, tid = WARD, source = ar_stl_race, sid = GEOID,
                               weight = "sum", output = "sf", extensive = "TOTAL_E"),
                "object 'ham' not found")
-  expect_error(aw_interpolate(aw_stl_wards, tid = WARD, source = ham, sid = GEOID,
+  expect_error(aw_interpolate(ar_stl_wards, tid = WARD, source = ham, sid = GEOID,
[…]

### 2018-12-17 tests/testthat/test_aw_intersect.R

@@ -3,32 +3,32 @@ context("test aw_intersect function")
 # load test data ------------------------------------------------
 
 # target data
-data(aw_stl_wards, package = "areal")
+data(ar_stl_wards, package = "areal")
 
 # source data
-data(aw_stl_race, package = "areal")
+data(ar_stl_race, package = "areal")
 
 # test errors ------------------------------------------------
 
 test_that("errors with missing objects", {
-  expect_error(aw_intersect(ham, source = aw_stl_race, areaVar = "area"),
+  expect_error(aw_intersect(ham, source = ar_stl_race, areaVar = "area"),
                "object 'ham' not found")
-  expect_error(aw_intersect(aw_stl_wards, source = ham, areaVar = "area"),
+  expect_error(aw_intersect(ar_stl_wards, source = ham, areaVar = "area"),
                "object 'ham' not found")
 })
 
 test_that("errors with missing parameters", {
-  expect_error(aw_intersect(source = aw_stl_race, areaVar = "area"),
+  expect_error(aw_intersect(source = ar_stl_race, areaVar = "area"),
                "A sf object containing target data must be specified for the '.data' argument.")
-  expect_error(aw_intersect(aw_stl_wards, areaVar = "area"),
+  expect_error(aw_intersect(ar_stl_wards, areaVar = "area"),
                "A sf object containing source data must be specified for the 'source' argument.")
-  expect_error(aw_intersect(aw_stl_wards, source = aw_stl_race),
+  expect_error(aw_intersect(ar_stl_wards, source = ar_stl_race),
                "A variable name must be specified for the 'areaVar' argument.")
 })
 
 # test inputs ------------------------------------------------
 
 test_that("correctly specified functions execute without error", {
-  expect_error(aw_intersect(aw_stl_wards, source = aw_stl_race, areaVar = "area"), NA)
-  expect_error(aw_intersect(aw_stl_wards, source = aw_stl_race, areaVar = area), NA)
+  expect_error(aw_intersect(ar_stl_wards, source = ar_stl_race, areaVar = "area"), NA)
+  expect_error(aw_intersect(ar_stl_wards, source = ar_stl_race, areaVar = area), NA)
 })

### 2018-12-17 tests/testthat/test_aw_preview_weights.R

@@ -3,19 +3,19 @@ context("test aw_preview_weights function")
 # load test data ------------------------------------------------
 
 # target data
-data(aw_stl_wards, package = "areal")
+data(ar_stl_wards, package = "areal")
 
 # source data
-data(aw_stl_race, package = "areal")
-data(aw_stl_asthma, package = "areal")
+data(ar_stl_race, package = "areal")
+data(ar_stl_asthma, package = "areal")
 
 ## create modified asthma data
-aw_stl_asthma %>%
+ar_stl_asthma %>%
   dplyr::select(-STATEFP, -COUNTYFP, -TRACTCE, -NAMELSAD, -ALAND, -AWATER) -> asthma
 
 ## create combined data
 ### remove sf geometry
-race <- aw_stl_race
+race <- ar_stl_race
 sf::st_geometry(race) <- NULL
 
 ### create combined data
@@ -26,69 +26,69 @@ race %>%
 # test errors ------------------------------------------------
 
 test_that("errors with missing objects", {
-  expect_error(aw_preview_weights(ham, tid = WARD, source = aw_stl_race, sid = GEOID, type = "extensive"),
+  expect_error(aw_preview_weights(ham, tid = WARD, source = ar_stl_race, sid = GEOID, type = "extensive"),
                "object 'ham' not found")
-  expect_error(aw_preview_weights(aw_stl_wards, tid = WARD, source = ham, sid = GEOID, type = "extensive"),
+  expect_error(aw_preview_weights(ar_stl_wards, tid = WARD, source = ham, sid = GEOID, type = "extensive"),
                "object 'ham' not found")
 })
 
 test_that("errors with missing parameters", {
-  expect_error(aw_preview_weights(tid = WARD, source = aw_stl_race, sid = GEOID, type = "extensive"),
+  expect_error(aw_preview_weights(tid = WARD, source = ar_stl_race, sid = GEOID, type = "extensive"),
                "A sf object containing target data must be specified for the '.data' argument.")
-  expect_error(aw_preview_weights(aw_stl_wards, source = aw_stl_race, sid = GEOID, type = "extensive"),
+  expect_error(aw_preview_weights(ar_stl_wards, source = ar_stl_race, sid = GEOID, type = "extensive"),
                "A variable name must be specified for the 'tid' argument.")
-  expect_error(aw_preview_weights(aw_stl_wards, tid = WARD, sid = GEOID, type = "extensive"),
[…]

### 2018-12-17 tests/testthat/test_aw_total.R

@@ -3,61 +3,61 @@ context("test aw_total function")
 # load test data ------------------------------------------------
 
 # target data
-data(aw_stl_wards, package = "areal")
+data(ar_stl_wards, package = "areal")
 
 # source data
-data(aw_stl_race, package = "areal")
+data(ar_stl_race, package = "areal")
 
 # calculate intersection
-aw_stl_wards %>%
-  aw_intersect(source = aw_stl_race, areaVar = "...area") -> intersect
+ar_stl_wards %>%
+  aw_intersect(source = ar_stl_race, areaVar = "...area") -> intersect
 
 # test errors ------------------------------------------------
 
 test_that("errors with missing objects", {
-  expect_error(aw_total(ham, source = aw_stl_race, id = GEOID, areaVar = "...area",
+  expect_error(aw_total(ham, source = ar_stl_race, id = GEOID, areaVar = "...area",
                             totalVar = "...totalArea", weight = "sum", type = "extensive"),
                "object 'ham' not found")
 })
 
 test_that("errors with missing parameters", {
-  expect_error(aw_total(source = aw_stl_race, id = GEOID, areaVar = "...area",
+  expect_error(aw_total(source = ar_stl_race, id = GEOID, areaVar = "...area",
                         totalVar = "...totalArea", weight = "sum", type = "extensive"),
                "A sf object containing intersected data must be specified for the '.data' argument.")
   expect_error(aw_total(intersect, id = GEOID, areaVar = "...area",
                         totalVar = "...totalArea", weight = "sum", type = "extensive"),
                "A sf object containing souce data must be specified for the 'source' argument.")
-  expect_error(aw_total(intersect, source = aw_stl_race, areaVar = "...area",
+  expect_error(aw_total(intersect, source = ar_stl_race, areaVar = "...area",
                         totalVar = "...totalArea", weight = "sum", type = "extensive"),
                "A variable name must be specified for the 'id' argument.")
-  expect_error(aw_total(intersect, source = aw_stl_race, id = GEOID,
+  expect_error(aw_total(intersect, source = ar_stl_race, id = GEOID,
                         totalVar = "...totalArea", weight = "sum", type = "extensive"),
                "A variable name must be specified for the 'areaVar' argument.")
-  expect_error(aw_total(intersect, source = aw_stl_race, id = GEOID, areaVar = "...area",
+  expect_error(aw_total(intersect, source = ar_stl_race, id = GEOID, areaVar = "...area",
[…]

### 2018-12-17 tests/testthat/test_aw_validate.R

@@ -3,71 +3,71 @@ context("test aw_validate function")
 # load test data ------------------------------------------------
 
 # target data
-data(aw_stl_wards, package = "areal")
+data(ar_stl_wards, package = "areal")
 
 # source data
-data(aw_stl_race, package = "areal")
+data(ar_stl_race, package = "areal")
 
 # test errors ------------------------------------------------
 
 test_that("errors with missing objects", {
-  expect_error(aw_validate(source = ham, target = aw_stl_wards, varList = "TOTAL_E"),
+  expect_error(aw_validate(source = ham, target = ar_stl_wards, varList = "TOTAL_E"),
                "object 'ham' not found")
-  expect_error(aw_validate(source = aw_stl_race, target = ham, varList = "TOTAL_E"),
+  expect_error(aw_validate(source = ar_stl_race, target = ham, varList = "TOTAL_E"),
                "object 'ham' not found")
 })
 
 test_that("errors with missing parameters", {
-  expect_error(aw_validate(target = aw_stl_wards, varList = "TOTAL_E"),
+  expect_error(aw_validate(target = ar_stl_wards, varList = "TOTAL_E"),
                "A sf object containing source data must be specified for the 'source' argument.")
-  expect_error(aw_validate(source = aw_stl_race, varList = "TOTAL_E"),
+  expect_error(aw_validate(source = ar_stl_race, varList = "TOTAL_E"),
                "A sf object containing target data must be specified for the 'target' argument.")
-  expect_error(aw_validate(source = aw_stl_race, target = aw_stl_wards),
+  expect_error(aw_validate(source = ar_stl_race, target = ar_stl_wards),
                "A variable name or vector of variable names must be specified for the 'varList' argument.")
 })
 
 test_that("errors with misspecified parameters", {
-  expect_error(aw_validate(source = aw_stl_race, target = aw_stl_wards, varList = "TOTAL_E", verbose = "ham"),
+  expect_error(aw_validate(source = ar_stl_race, target = ar_stl_wards, varList = "TOTAL_E", verbose = "ham"),
[…]

### 2018-12-17 tests/testthat/test_aw_verify.R

@@ -3,16 +3,16 @@ context("test aw_verify function")
 # load test data ------------------------------------------------
 
 # target data
-data(aw_stl_wards, package = "areal")
+data(ar_stl_wards, package = "areal")
 
 # source data
-data(aw_stl_race, package = "areal")
+data(ar_stl_race, package = "areal")
 
 # interpolate data
-totalResult1 <- aw_interpolate(aw_stl_wards, tid = WARD, source = aw_stl_race, sid = GEOID,
+totalResult1 <- aw_interpolate(ar_stl_wards, tid = WARD, source = ar_stl_race, sid = GEOID,
                                weight = "sum", output = "sf", extensive = "TOTAL_E")
 
-totalResult2 <- aw_interpolate(aw_stl_wards, tid = WARD, source = aw_stl_race, sid = GEOID,
+totalResult2 <- aw_interpolate(ar_stl_wards, tid = WARD, source = ar_stl_race, sid = GEOID,
                               weight = "total", output = "sf", extensive = "TOTAL_E")
 
 # test errors ------------------------------------------------
@@ -20,26 +20,26 @@ totalResult2 <- aw_interpolate(aw_stl_wards, tid = WARD, source = aw_stl_race, s
 test_that("errors with missing objects", {
   expect_error(aw_verify(source = ham, sourceValue = TOTAL_E, result = totalResult1, resultValue = TOTAL_E),
                "object 'ham' not found")
-  expect_error(aw_verify(source = aw_stl_race, sourceValue = TOTAL_E, result = ham, resultValue = TOTAL_E),
+  expect_error(aw_verify(source = ar_stl_race, sourceValue = TOTAL_E, result = ham, resultValue = TOTAL_E),
                "object 'ham' not found")
 })
 
 test_that("errors with missing parameters", {
   expect_error(aw_verify(sourceValue = TOTAL_E, result = totalResult1, resultValue = TOTAL_E),
                "A sf object containing source data must be specified for the 'source' argument.")
-  expect_error(aw_verify(source = aw_stl_race, result = totalResult1, resultValue = TOTAL_E),
+  expect_error(aw_verify(source = ar_stl_race, result = totalResult1, resultValue = TOTAL_E),
                "A variable name must be specified for the 'sourceValue' argument.")
-  expect_error(aw_verify(source = aw_stl_race, sourceValue = TOTAL_E, resultValue = TOTAL_E),
[…]

### 2018-12-17 tests/testthat/test_aw_weight.R

@@ -3,15 +3,15 @@ context("test aw_weight function")
 # load test data ------------------------------------------------
 
 # target data
-data(aw_stl_wards, package = "areal")
+data(ar_stl_wards, package = "areal")
 
 # source data
-data(aw_stl_race, package = "areal")
+data(ar_stl_race, package = "areal")
 
 # calculate intersection
-aw_stl_wards %>%
-  aw_intersect(source = aw_stl_race, areaVar = "...area") %>%
-  aw_total(source = aw_stl_race, id = GEOID, areaVar = "...area",
+ar_stl_wards %>%
+  aw_intersect(source = ar_stl_race, areaVar = "...area") %>%
+  aw_total(source = ar_stl_race, id = GEOID, areaVar = "...area",
            totalVar = "...totalArea", weight = "sum", type = "extensive")-> intersect
 
 # test errors ------------------------------------------------

### 2018-12-17 README.Rmd
continued work on README, pkgdown site, and vignettes

@@
 
-Areal interpolation is the process making estimates about the population features from a source set of polygons to an overlapping but incongruent set of target polygons.
+Areal interpolation is the process making estimates from a source set of polygons to an overlapping but incongruent set of target polygons.
 One challenge with areal interpolation is that, while the processes themselves are well documented, implementing them often involves "reinventing the wheel." Within `R`, the `sf` package does offer a basic interface for areal weighted interpolation (`st_interpolate_aw`).

### 2018-12-17 index.Rmd
rebuild site

@@
 
-## Installation
-### Installing Dependencies
-You should check the [`sf` package website](https://r-spatial.github.io/sf/) for the latest details on installing dependencies for that package.
-Instructions vary significantly by operating system.
-For best results, have `sf` installed before you install `areal`.
-Other dependencies, like `dplyr`, will be installed automatically with `areal` if they are not already present.
-
-The one exception here is the dependency `lwgeom`, which Linux users will need to follow some [spatial instructions](https://github.com/r-spatial/lwgeom) to install correctly.
-
-### Installing areal
-The development version of `areal` can be accessed from Github with `remotes`:
-
-```r
-# install.packages("remotes")
-remotes::install_github("slu-openGIS/areal")
-```
+## Resources
+* The [Get started](/areal/) article has:
+    * a quick overview of getting up and running with `areal` including **installation tips**,
+    * some notes on **preparing data** for interpolation,
+    * a brief introduction to the **`aw_interpolate()` function**,
+    * tips for **getting help**, **submitting feedback**, 
+    * and the `areal` package's development roadmap!
+* Additional details about preparing data are available in a [dedicated article](/data-preparation/).
+* The areal weighted interpolation process is described in-depth in a [dedicated article](/areal-weighted-interpolation/).
 

### 2018-12-18 README.Rmd
add example map to README and areal vig

@@
 
+What results from `aw_interpolate()` is mapped below.
+Total population per census tract in St.
+Louis is mapped on the left in panel A.
+Using `aw_interpolate()` as we did in the previous example, we estimate population counts for Wards in St.
+Louis from those census tract values.
+These estimated values are mapped on the right in panel B.
+
+```{r exampleMap, echo=FALSE, out.width = '100%'}
+knitr::include_graphics("man/figures/exampleMap.png")
+```
+
 Both extensive and intensive data can be interpolated simultaneously by using both the `extensive` and `intensive` arguments.

### 2018-12-18 index.Rmd
add example map to README and areal vig

@@
 ## Resources
-* The [Get started](/areal/) article has:
+* The [Get started](articles/areal.html) article has:
     * a quick overview of getting up and running with `areal` including **installation tips**,
@@
     * and the `areal` package's development roadmap!
-* Additional details about preparing data are available in a [dedicated article](/data-preparation/).
-* The areal weighted interpolation process is described in-depth in a [dedicated article](/areal-weighted-interpolation/).
+* Additional details about preparing data are available in a [dedicated article](articles/data-preparation.html).
+* The areal weighted interpolation process is described in-depth in a [dedicated article](articles/areal-weighted-interpolation.html).
 

### 2018-12-18 inst/extdata/readmeFigure.R

@@ -1,0 +1,38 @@
+# create map for README, areal vignette
+
+library(areal)
+library(ggplot2)
+library(cowplot)
+library(viridis)
+library(prener)
+library(here)
+
+result <- aw_interpolate(ar_stl_wards, tid = WARD, source = ar_stl_race, sid = "GEOID",
+                         weight = "sum", output = "sf", extensive = "TOTAL_E")
+
+p1 <- ggplot() +
+  geom_sf(ar_stl_race, mapping = aes(fill = TOTAL_E)) +
+  scale_fill_viridis() +
+  labs(
+    title = "Total Population per Tract",
+    subtitle = "St. Louis, MO (2017)"
+  ) +
+  cp_sequoiaTheme(base_size = 18, background = "white", map = TRUE) +
+  theme(legend.key.size = unit(1, units="cm"))
+
+p2 <- ggplot() +
+  geom_sf(result, mapping = aes(fill = TOTAL_E)) +
+  scale_fill_viridis(option="plasma") +
+  labs(
+    title = "Total Population per Ward",
+    subtitle = "St. Louis, MO (2017)"
+  ) +
+  cp_sequoiaTheme(base_size = 18, background = "white", map = TRUE) +
+  theme(legend.key.size = unit(1, units="cm"))
+
+theme_set(theme_cowplot(font_family = "sans"))
+
+exampleMap <- plot_grid(p1, p2, labels = c("(A)", "(B)"))
+
+ggsave(filename = here("man", "figures", "exampleMap.png"), exampleMap,
+       width = cp_points(800, units = "in"), height = cp_points(450, units = "in"), dpi = 72)

### 2018-12-18 README.Rmd
clarifying language on homepage and get started article

@@
 Areal interpolation is the process making estimates from a source set of polygons to an overlapping but incongruent set of target polygons.
-One challenge with areal interpolation is that, while the processes themselves are well documented, implementing them often involves "reinventing the wheel." Within `R`, the `sf` package does offer a basic interface for areal weighted interpolation (`st_interpolate_aw`).
+One challenge with areal interpolation is that, while the processes themselves are well documented in the academic literature, implementing them often involves "reinventing the wheel." While the `R` package `sf` does offer a basic interface for areal weighted interpolation (`st_interpolate_aw`), it lacks some features that we use in our work.
 The `areal` package contains a suite tools for validation and estimation, providing a full-featured workflow that fits into both modern data management (e.g.

### 2018-12-18 index.Rmd
clarifying language on homepage and get started article

--- 2018-12-17 index.Rmd
@@
 
+## Quick Start
+If the `sf` package is already installed, the development version of `areal` can be accessed from Github with `remotes`:
+
+```r
+# install.packages("remotes")
+remotes::install_github("slu-openGIS/areal")
+```
+
+Additional details, including some tips for installing `sf`, can be found in the [Get started article](articles/areal.html#getting-started).
+
 ## Resources
-* The [Get started](/areal/) article has:
-    * a quick overview of getting up and running with `areal` including **installation tips**,
-    * some notes on **preparing data** for interpolation,
-    * a brief introduction to the **`aw_interpolate()` function**,
-    * tips for **getting help**, **submitting feedback**, 
+In addition to instructions for installation, the main [Get started](articles/areal.html) article has:
+
+  * a quick overview of areal interpolation,
+  * some notes on preparing data for interpolation,
+  * a brief introduction to the `aw_interpolate()` function,
+  * tips for getting help and submitting feedback, 
   * and the `areal` package's development roadmap!
-* Additional details about preparing data are available in a [dedicated article](/data-preparation/).
-* The areal weighted interpolation process is described in-depth in a [dedicated article](/areal-weighted-interpolation/).
 
-## Contributor Code of Conduct
-Please note that this project is released with a [Contributor Code of Conduct](.github/CODE_OF_CONDUCT.md). By participating in this project you agree to abide by its terms.
+This site also offers dedicated articles on [data preparation](articles/data-preparation.html) and [using `areal` for areal weighted interpolation](articles/areal-weighted-interpolation.html).

### 2018-12-18 R/ar_validate.R
convert to ar_validate

@@ -1,14 +1,17 @@
 #' Valdating Data for Interpolation
 #'
-#' @description \code{aw_validate} executes a series of logic tests for \code{sf} object status,
+#' @description \code{ar_validate} executes a series of logic tests for \code{sf} object status,
 #'     shared coordinates between source and target data, appropriate project, and absence of
 #'     variable name conflicts.
 #'
-#' @usage aw_validate(source, target, varList, verbose = FALSE)
+#' @usage ar_validate(source, target, varList, method = "aw", verbose = FALSE)
 #'
 #' @param source A \code{sf} object with data to be interpolated
 #' @param target A \code{sf} object that data should be interpolated to
 #' @param varList A vector of variable names to be added to the \code{target} object
+#' @param method The areal interpolation method validation is being performed for. This
+#'     should be set to \code{"aw"}. Additional functionality will be added as the package
+#'     adds new interpolation techniques.
 #' @param verbose A logical scalar; if \code{TRUE}, a tibble with test results is returned
 #'
 #' @return If \code{verbose} is \code{FALSE}, a logical scalar is returned that is \code{TRUE}
@@ -18,7 +21,7 @@
 #' @importFrom glue glue
 #'
 #' @export
-aw_validate <- function(source, target, varList, verbose = FALSE){
+ar_validate <- function(source, target, varList, method = "aw", verbose = FALSE){
 
   # check for missing parameters
   if (missing(source)) {
@@ -37,8 +40,12 @@ aw_validate <- function(source, target, varList, verbose = FALSE){
     stop("The 'verbose' argument must be either 'TRUE' or 'FALSE'.")
   }
 
+  if (method != "aw"){
+    stop("The 'method' argument must be 'aw'.")
+  }
+
   # store results from primary validate subfunctions
-  sf_result <- aw_validate_sf(source, target)
+  sf_result <- ar_validate_sf(source, target)
 
   # execute additional tests if both are sf, otherwise set results to NA
   if (sf_result == FALSE){
@@ -52,17 +59,17 @@ aw_validate <- function(source, target, varList, verbose = FALSE){
   } else if (sf_result == TRUE){
 
     # do both source and target have same CRS?
-    crs_result <- aw_validate_crs(source, target)
+    crs_result <- ar_validate_crs(source, target)
 
     # are both source and target CRS values in planar?
[…]

### 2018-12-18 R/aw_interpolate.R

@@ -138,7 +138,7 @@ aw_interpolate <- function(.data, tid, source, sid, weight = "sum", output = "sf
   }
 
   # validate source and target data
-  if (aw_validate(source = source, target = .data, varList = vars) == FALSE){
+  if (ar_validate(source = source, target = .data, varList = vars, method = "aw") == FALSE){
     stop("Data validation failed. Use aw_validate with verbose = TRUE to identify concerns.")
   }
 

### 2018-12-18 tests/testthat/test_ar_validate.R

@@ -1,0 +1,106 @@
+context("test ar_validate function")
+
+# load test data ------------------------------------------------
+
+# target data
+data(ar_stl_wards, package = "areal")
+
+# source data
+data(ar_stl_race, package = "areal")
+
+# test errors ------------------------------------------------
+
+test_that("errors with missing objects", {
+  expect_error(ar_validate(source = ham, target = ar_stl_wards, varList = "TOTAL_E", method = "aw"),
+               "object 'ham' not found")
+  expect_error(ar_validate(source = ar_stl_race, target = ham, varList = "TOTAL_E", method = "aw"),
+               "object 'ham' not found")
+})
+
+test_that("errors with missing parameters", {
+  expect_error(ar_validate(target = ar_stl_wards, varList = "TOTAL_E", method = "aw"),
+               "A sf object containing source data must be specified for the 'source' argument.")
+  expect_error(ar_validate(source = ar_stl_race, varList = "TOTAL_E", method = "aw"),
+               "A sf object containing target data must be specified for the 'target' argument.")
+  expect_error(ar_validate(source = ar_stl_race, target = ar_stl_wards, method = "aw"),
+               "A variable name or vector of variable names must be specified for the 'varList' argument.")
+})
+
+test_that("errors with misspecified parameters", {
+  expect_error(ar_validate(source = ar_stl_race, target = ar_stl_wards, varList = "TOTAL_E",
+                           method = "aw", verbose = "ham"),
+               "The 'verbose' argument must be either 'TRUE' or 'FALSE'.")
+})
+
+# test inputs ------------------------------------------------
+
+test_that("correctly specified functions execute without error", {
+  expect_equal(ar_validate(source = ar_stl_race, target = ar_stl_wards, method = "aw",
+                           varList = c("TOTAL_E", "BLACK_E")), TRUE)
+})
+
+# test validation failures ------------------------------------------------
+
+wardsdf <- ar_stl_wards
+sf::st_geometry(wardsdf) <- NULL
+
+racedf <- ar_stl_race
+sf::st_geometry(racedf) <- NULL
+
[…]

### 2018-12-18 tests/testthat/test_aw_validate.R

@@ -1,103 +1,0 @@
-context("test aw_validate function")
-
-# load test data ------------------------------------------------
-
-# target data
-data(ar_stl_wards, package = "areal")
-
-# source data
-data(ar_stl_race, package = "areal")
-
-# test errors ------------------------------------------------
-
-test_that("errors with missing objects", {
-  expect_error(aw_validate(source = ham, target = ar_stl_wards, varList = "TOTAL_E"),
-               "object 'ham' not found")
-  expect_error(aw_validate(source = ar_stl_race, target = ham, varList = "TOTAL_E"),
-               "object 'ham' not found")
-})
-
-test_that("errors with missing parameters", {
-  expect_error(aw_validate(target = ar_stl_wards, varList = "TOTAL_E"),
-               "A sf object containing source data must be specified for the 'source' argument.")
-  expect_error(aw_validate(source = ar_stl_race, varList = "TOTAL_E"),
-               "A sf object containing target data must be specified for the 'target' argument.")
-  expect_error(aw_validate(source = ar_stl_race, target = ar_stl_wards),
-               "A variable name or vector of variable names must be specified for the 'varList' argument.")
-})
-
-test_that("errors with misspecified parameters", {
-  expect_error(aw_validate(source = ar_stl_race, target = ar_stl_wards, varList = "TOTAL_E", verbose = "ham"),
-               "The 'verbose' argument must be either 'TRUE' or 'FALSE'.")
-})
-
-# test inputs ------------------------------------------------
-
-test_that("correctly specified functions execute without error", {
-  expect_equal(aw_validate(source = ar_stl_race, target = ar_stl_wards, varList = c("TOTAL_E", "BLACK_E")), TRUE)
-})
-
-# test validation failures ------------------------------------------------
-
-wardsdf <- ar_stl_wards
-sf::st_geometry(wardsdf) <- NULL
-
-racedf <- ar_stl_race
-sf::st_geometry(racedf) <- NULL
-
-wards83 <- sf::st_transform(ar_stl_wards, crs = 4269)
-race83 <- sf::st_transform(ar_stl_race, crs = 4269)
-
[…]

### 2018-12-18 README.Rmd
attempt to update pkgdown site

@@
 ## Usage 
+Two function prefixes are used in `areal` to allow users to take advantage of RStudio's auto complete functionality:
+
+* `ar_` - data and functions that are used for multiple interpolation methods
+* `aw_` - functions that are used specifically for areal weighted interpolation
+
 ### Data

### 2018-12-18 README.Rmd
get vignette building
fix typo and add link to website

@@
 ### Installing Dependencies
-You should check the [`sf` package website](https://r-spatial.github.io/sf/) for the latest details on installing dependencies for that package.
+You should check the [`sf` package website](https://r-spatial.github.io/sf/) and the [`areal` package website](https://slu-openGIS.github.io/area/) for the latest details on installing dependencies for that package.
 Instructions vary significantly by operating system.
@@
 
-The one exception here is the dependency `lwgeom`, which Linux users will need to follow some [spatial instructions](https://github.com/r-spatial/lwgeom) to install correctly.
+The one exception here is the dependency `lwgeom`, which Linux users will need to follow some [special instructions](https://github.com/r-spatial/lwgeom) to install correctly.
 
@@
 >
-> race <- aw_stl_race
-> asthma <- aw_stl_asthma
-> wards <- aw_stl_wards
+> race <- ar_stl_race
+> asthma <- ar_stl_asthma
+> wards <- ar_stl_wards
 ```

### 2018-12-18 tests/testthat/test_ar_validate.R
add test to ar_validate method arg

@@ -30,6 +30,9 @@ test_that("errors with misspecified parameters", {
   expect_error(ar_validate(source = ar_stl_race, target = ar_stl_wards, varList = "TOTAL_E",
                            method = "aw", verbose = "ham"),
                "The 'verbose' argument must be either 'TRUE' or 'FALSE'.")
+  expect_error(ar_validate(source = ar_stl_race, target = ar_stl_wards, varList = "TOTAL_E",
+                           method = "ham", verbose = FALSE),
+               "The 'method' argument must be 'aw'.")
 })
 
 # test inputs ------------------------------------------------

### 2018-12-18 R/aw_aggregate.R
clarify function titles

@@ -1,4 +1,4 @@
-#' Aggregate new field of interest by target IDs
+#' Aggregate Estimates Based on Target ID
 #'
 #' @description \code{aw_aggregate} sums the new estimates produced by \link{aw_calculate}
 #'     based on the target id. These are then joined with the target data. This is

### 2018-12-18 R/aw_calculate.R

@@ -1,4 +1,4 @@
-#' Make field new variable
+#' Caclulate Estimated Population
 #'
 #' @description \code{aw_calculate} multiplies the given \code{value} by the area weight. This
 #'     is the fourth step in the interpolation process after \link{aw_weight}.

### 2018-12-18 R/aw_total.R

@@ -1,4 +1,4 @@
-#' Create new total area field in intersection
+#' Calculate Total Area
 #'
 #' @description \code{aw_total} produces a new total area field that contains
 #'     the total area by \code{source} id. This is the second step in the

### 2018-12-18 R/aw_weight.R

@@ -1,4 +1,4 @@
-#' Calculate area weight using source ID areas
+#' Calculate Areal Weight
 #'
 #' @description \code{aw_weight} creates an area weight field by dividing the area
 #'     field by the total area field. This is the third step in the interpolation

### 2018-12-19 inst/extdata/awFigure.R
developing aw vignette

@@ -1,0 +1,47 @@
+# create map for README, areal vignette
+
+library(areal)
+library(sf)
+library(ggplot2)
+library(cowplot)
+library(prener)
+library(here)
+
+p1 <- ggplot() +
+  geom_sf(data = ar_stl_race, fill = "#000000", color = "#ffffff") +
+  labs(
+    title = "Census Tract Features",
+    subtitle = "St. Louis, MO"
+  ) +
+  cp_sequoiaTheme(base_size = 14, background = "white", map = TRUE) +
+  theme(legend.position="none")
+
+p2 <- ggplot() +
+  geom_sf(data = ar_stl_wards, fill = "#000000", color = "#ffffff") +
+  labs(
+    title = "2010 Ward Features",
+    subtitle = "St. Louis, MO"
+  ) +
+  cp_sequoiaTheme(base_size = 14, background = "white", map = TRUE) +
+  theme(legend.position="none")
+
+theme_set(theme_cowplot(font_family = "sans", font_size = 14))
+
+exampleMap <- plot_grid(p1, p2, labels = c("(A)", "(B)"))
+
+ggplot2::ggsave(filename = here("man", "figures", "featureMap.png"), exampleMap,
+       width = cp_points(800, units = "in"), height = cp_points(450, units = "in"), dpi = 72)
+
+intersect <- st_intersection(ar_stl_race, ar_stl_wards)
+
+p3 <- ggplot() +
+  geom_sf(data = intersect, fill = "#000000", color = "#ffffff") +
+  labs(
+    title = "Intersected Features",
+    subtitle = "St. Louis, MO"
+  ) +
+  cp_sequoiaTheme(base_size = 14, background = "white", map = TRUE) +
+  theme(legend.position="none")
+
+ggplot2::ggsave(filename = here("man", "figures", "intersectMap.png"), p3,
+                width = cp_points(500, units = "in"), height = cp_points(450, units = "in"), dpi = 72)

### 2018-12-19 inst/extdata/readmeFigure.R

@@ -17,7 +17,7 @@ p1 <- ggplot() +
     title = "Total Population per Tract",
     subtitle = "St. Louis, MO (2017)"
   ) +
-  cp_sequoiaTheme(base_size = 18, background = "white", map = TRUE) +
+  cp_sequoiaTheme(base_size = 14, background = "white", map = TRUE) +
   theme(legend.key.size = unit(1, units="cm"))
 
 p2 <- ggplot() +
@@ -27,12 +27,12 @@ p2 <- ggplot() +
     title = "Total Population per Ward",
     subtitle = "St. Louis, MO (2017)"
   ) +
-  cp_sequoiaTheme(base_size = 18, background = "white", map = TRUE) +
+  cp_sequoiaTheme(base_size = 14, background = "white", map = TRUE) +
   theme(legend.key.size = unit(1, units="cm"))
 
-theme_set(theme_cowplot(font_family = "sans"))
+theme_set(theme_cowplot(font_family = "sans", font_size = 14))
 
 exampleMap <- plot_grid(p1, p2, labels = c("(A)", "(B)"))
 
-ggsave(filename = here("man", "figures", "exampleMap.png"), exampleMap,
+ggplot2::ggsave(filename = here("man", "figures", "exampleMap.png"), exampleMap,
        width = cp_points(800, units = "in"), height = cp_points(450, units = "in"), dpi = 72)

### 2018-12-19 inst/extdata/awFigure.R
complete draft aw article

@@ -45,3 +45,17 @@ p3 <- ggplot() +
 
 ggplot2::ggsave(filename = here("man", "figures", "intersectMap.png"), p3,
                 width = cp_points(500, units = "in"), height = cp_points(450, units = "in"), dpi = 72)
+
+p4 <- ggplot() +
+  geom_sf(data = ar_stl_race, fill = "#ff0000", color = "#000000") +
+  geom_sf(data = ar_stl_wardsClipped, fill = "#ffffff", color = "#000000") +
+  labs(
+    title = "Wards Clipped / Tracts Overlap",
+    subtitle = "St. Louis, MO"
+  ) +
+  cp_sequoiaTheme(base_size = 14, background = "white", map = TRUE) +
+  theme(legend.position="none")
+
+ggplot2::ggsave(filename = here("man", "figures", "overlapMap.png"), p4,
+                width = cp_points(500, units = "in"), height = cp_points(450, units = "in"), dpi = 72)
+

### 2018-12-19 inst/extdata/awFigure.R
adjust display of aw article images

@@ -43,19 +43,22 @@ p3 <- ggplot() +
   cp_sequoiaTheme(base_size = 14, background = "white", map = TRUE) +
   theme(legend.position="none")
 
-ggplot2::ggsave(filename = here("man", "figures", "intersectMap.png"), p3,
-                width = cp_points(500, units = "in"), height = cp_points(450, units = "in"), dpi = 72)
+intersectMap <- plot_grid(p3, NULL, labels = c("(C)"))
+
+ggplot2::ggsave(filename = here("man", "figures", "intersectMap.png"), intersectMap,
+                width = cp_points(800, units = "in"), height = cp_points(450, units = "in"), dpi = 72)
 
 p4 <- ggplot() +
   geom_sf(data = ar_stl_race, fill = "#ff0000", color = "#000000") +
   geom_sf(data = ar_stl_wardsClipped, fill = "#ffffff", color = "#000000") +
   labs(
-    title = "Wards Clipped / Tracts Overlap",
+    title = "Clipped Wards Overlaid on Tracts",
     subtitle = "St. Louis, MO"
   ) +
   cp_sequoiaTheme(base_size = 14, background = "white", map = TRUE) +
   theme(legend.position="none")
 
-ggplot2::ggsave(filename = here("man", "figures", "overlapMap.png"), p4,
-                width = cp_points(500, units = "in"), height = cp_points(450, units = "in"), dpi = 72)
+overlapMap <- plot_grid(p4, NULL, labels = c("(D)"))
 
+ggplot2::ggsave(filename = here("man", "figures", "overlapMap.png"), overlapMap,
+                width = cp_points(800, units = "in"), height = cp_points(450, units = "in"), dpi = 72)

### 2018-12-19 README.Rmd
add Zenodo badge

@@
 [![Coverage status](https://codecov.io/gh/slu-openGIS/areal/branch/master/graph/badge.svg)](https://codecov.io/github/slu-openGIS/areal?branch=master)
+[![DOI](https://zenodo.org/badge/152279647.svg)](https://zenodo.org/badge/latestdoi/152279647)
 [![CRAN_status_badge](http://www.r-pkg.org/badges/version/areal)](https://cran.r-project.org/package=areal)

### 2018-12-20 README.Rmd
replace logo

@@
 Areal interpolation is the process making estimates from a source set of polygons to an overlapping but incongruent set of target polygons.
-One challenge with areal interpolation is that, while the processes themselves are well documented in the academic literature, implementing them often involves "reinventing the wheel." While the `R` package `sf` does offer a basic interface for areal weighted interpolation (`st_interpolate_aw`), it lacks some features that we use in our work.
+One challenge with areal interpolation is that, while the processes themselves are well documented in the academic literature, implementing them often involves "reinventing the wheel" by re-creating the process in the analyst's tool choice.
+
+While the `R` package `sf` does offer a basic interface for areal weighted interpolation (`st_interpolate_aw`), it lacks some features that we use in our work.
 The `areal` package contains a suite tools for validation and estimation, providing a full-featured workflow that fits into both modern data management (e.g.

### 2018-12-20 R/ar_validate.R
spellcheck

@@ -1,4 +1,4 @@
-#' Valdating Data for Interpolation
+#' Validating Data for Interpolation
 #'
 #' @description \code{ar_validate} executes a series of logic tests for \code{sf} object status,
 #'     shared coordinates between source and target data, appropriate project, and absence of

### 2018-12-20 R/aw_calculate.R

@@ -1,4 +1,4 @@
-#' Caclulate Estimated Population
+#' Calculate Estimated Population
 #'
 #' @description \code{aw_calculate} multiplies the given \code{value} by the area weight. This
 #'     is the fourth step in the interpolation process after \link{aw_weight}.
@@ -7,7 +7,7 @@
 #'
 #' @param .data A given intersected dataset
 #' @param value A column within \code{source} to be interpolated
-#' @param areaWeight The name of the variable containg area weight per feature
+#' @param areaWeight The name of the variable containing area weight per feature
 #' @param newVar Optional; a new field name to store the interpolated value in. If not specified,
 #'     the \code{value} argument will be used as the new field name.
 #'

### 2018-12-20 R/aw_interpolate.R

@@ -1,8 +1,8 @@
 #' Interpolate Values
 #'
-#' @description This is the core function within the package. It evalues both the input
-#'     data sources and validates them before interpolating one or more listed values
-#'     from the source data into the target data.
+#' @description This is the core function within the package for areal weighted
+#'     interpolation. It validates both data sources before interpolating one or more
+#'     listed values from the source data into the target data.
 #'
 #' @usage aw_interpolate(.data, tid, source, sid, weight = "sum", output = "sf", extensive,
 #'     intensive)
@@ -22,9 +22,9 @@
 #'     \code{"sum"}. For \code{"intensive"} interpolations, should be \code{"sum"}. For mixed
 #'     interpolations, this will only impact the calculation of the extensive variables.
 #' @param output One of either \code{"sf"} or \code{"tibble"}
-#' @param extensive A vector of quoted variable names to be treated as spatiall extensive
+#' @param extensive A vector of quoted variable names to be treated as spatially extensive
 #'     (e.g. population counts); optional if \code{intensive} is specified
-#' @param intensive A vector of quoted variable names to be treated as spatiall intensive
+#' @param intensive A vector of quoted variable names to be treated as spatially intensive
 #'     (e.g. population density); optional if \code{extensive} is specified
 #'
 #' @return A \code{sf} object or a \code{tibble} with the value or values interpolated into
@@ -235,7 +235,7 @@ aw_interpolate <- function(.data, tid, source, sid, weight = "sum", output = "sf
 #' @param value A column within \code{source} to be interpolated
 #' @param target A \code{sf} object that data should be interpolated to
 #' @param tid A unique identification number within \code{target}
-#' @param type One of either \code{"extensive"} (if the data are spatitally extensive e.g.
+#' @param type One of either \code{"extensive"} (if the data are spatially extensive e.g.
 #'     population counts), \code{"intensive"} (if the data are spatially intensive e.g.
 #'     population density), or \code{"mixed"} (if the data include both extensive and
 #'     intensive values). If \code{"extensive"}, the sum is returned for the interpolated
@@ -288,7 +288,7 @@ aw_interpolate_single <- function(source, sid, value, target, tid, type, weight)
 #' @param values A vector of columns within \code{source} to be interpolated
 #' @param target A \code{sf} object that data should be interpolated to
 #' @param tid A unique identification number within \code{target}
-#' @param type One of either \code{"extensive"} (if the data are spatitally extensive e.g.
[…]

### 2018-12-20 R/aw_verify.R

@@ -1,7 +1,7 @@
 #' Verify Correct Extensive-Sum Interpolation
 #'
 #' @details \code{aw_verify} ensures that the sum of the resulting interpolated
-#'     value is equal to the sum of the origina source value. This functionality
+#'     value is equal to the sum of the original source value. This functionality
 #'     only works for interpolations that are extensive and use the \code{sum}
 #'     approach to calculating areal weights.
 #'

### 2018-12-20 R/aw_weight.R

@@ -8,7 +8,7 @@
 #'
 #' @param .data A \code{sf} object that has been intersected using \link{aw_intersect}
 #' @param areaVar The name of the variable measuring a feature's area
-#' @param totalVar The name of the variable containg total area field by \code{source} id
+#' @param totalVar The name of the variable containing total area field by \code{source} id
 #' @param areaWeight The name of a new area weight field to be calculated
 #'
 #' @return A \code{sf} object with the intersected data and new area weight field.

### 2019-01-01 index.Rmd
spellcheck

@@
 ## Quick Start
-If the `sf` package is already installed, the development version of `areal` can be accessed from Github with `remotes`:
+If the `sf` package is already installed, the easiest way to get `areal` is to install it from CRAN:
+
+``` r
+install.packages("areal")
+```
+
+Alternatively, the development version of `areal` can be accessed from GitHub with `remotes`:
 

### 2019-01-01 README.Rmd
spellcheck

@@
 
+## Bug Fixes in v0.1.3
+The initial CRAN release contains two known bugs (see Issues [6](https://github.com/slu-openGIS/areal/issues/6) and [7](https://github.com/slu-openGIS/areal/issues/7)), both of which are fixed in the current GitHub release:
+
+1.
+If the `tid` and `sid` column names are identical, the interpolated column created by `aw_interpolate()` will consist of all `NA` values.
+The simplest workaround is to rename either `tid` or `sid` before executing `aw_interpolate()`.
+Alternatively, you can install the development version of `areal` from GitHub.
+2.
+Some intersections of `sf` geometries will result in geometry collections being created.
+This appears to be an infrequent issue, but it will result in an error when `aw_interpolate()` is executed.
+The error will begin with `Warning in st_cast.GEOMETRYCOLLECTION(X[[i]], ...)`.
+The simplest workaround is to install the development version of `areal` from GitHub.
+
+Big thanks to early adopter [Matt Herman](https://github.com/mfherman) for catching both of these!
+
 ## Installation
@@
 ### Installing areal
-The development version of `areal` can be accessed from Github with `remotes`:
+The easiest way to get `areal` is to install it from CRAN:
+
+``` r
+install.packages("areal")
+```
+
+The development version of `areal` can be accessed from GitHub with `remotes`:
 

### 2019-01-01 index.Rmd

@@
 
+## Bug Fixes in v0.1.3
+The initial CRAN release contains two known bugs (see Issues [6](https://github.com/slu-openGIS/areal/issues/6) and [7](https://github.com/slu-openGIS/areal/issues/7)), both of which are fixed in the current GitHub release:
+
+1.
+If the `tid` and `sid` column names are identical, the interpolated column created by `aw_interpolate()` will consist of all `NA` values.
+The simplest workaround is to rename either `tid` or `sid` before executing `aw_interpolate()`.
+Alternatively, you can install the development version of `areal` from GitHub.
+2.
+Some intersections of `sf` geometries will result in geometry collections being created.
+This appears to be an infrequent issue, but it will result in an error when `aw_interpolate()` is executed.
+The error will begin with `Warning in st_cast.GEOMETRYCOLLECTION(X[[i]], ...)`.
+The simplest workaround is to install the development version of `areal` from GitHub.
+
+Big thanks to early adopter [Matt Herman](https://github.com/mfherman) for catching both of these!
+
 ## Quick Start

### 2019-01-01 index.Rmd
clarify github master branch language

@@
 ## Bug Fixes in v0.1.3
-The initial CRAN release contains two known bugs (see Issues [6](https://github.com/slu-openGIS/areal/issues/6) and [7](https://github.com/slu-openGIS/areal/issues/7)), both of which are fixed in the current GitHub release:
+The initial CRAN release contains two known bugs (see Issues [6](https://github.com/slu-openGIS/areal/issues/6) and [7](https://github.com/slu-openGIS/areal/issues/7)), both of which are fixed on the current GitHub master branch:
 

### 2019-01-02 README.Rmd
fix broken link in README.Rmd as well

@@
 ### Installing Dependencies
-You should check the [`sf` package website](https://r-spatial.github.io/sf/) and the [`areal` package website](https://slu-openGIS.github.io/area/) for the latest details on installing dependencies for that package.
+You should check the [`sf` package website](https://r-spatial.github.io/sf/) and the [`areal` package website](https://slu-openGIS.github.io/areal/) for the latest details on installing dependencies for that package.
 Instructions vary significantly by operating system.

### 2019-03-22 R/aw_intersect.R
performance improvement

@@ -65,11 +65,13 @@ aw_intersect <- function(.data, source, areaVar) {
   intersection %>%
     aw_area(areaVar = !!areaVarQ) -> intersection
 
-  intersection <- sf::st_collection_extract(intersection)
-  out <- sf::st_cast(intersection, "MULTIPOLYGON")
+  if(any(grepl("GEOMETRY", intersection))) {
+    intersection <- sf::st_collection_extract(intersection) %>%
+      sf::st_cast("MULTIPOLYGON")
+  }
 
   # return output
-  return(out)
+  return(intersection)
 
 }
 

### 2019-03-22 README.Rmd

@@
 ## Bug Fixes in v0.1.3
-The initial CRAN release contains two known bugs (see Issues [6](https://github.com/slu-openGIS/areal/issues/6) and [7](https://github.com/slu-openGIS/areal/issues/7)), both of which are fixed on the current GitHub master branch:
+The initial CRAN release contains four known bugs (see Issues [6](https://github.com/slu-openGIS/areal/issues/6), [7](https://github.com/slu-openGIS/areal/issues/7), [14](https://github.com/slu-openGIS/areal/issues/14), and [16](https://github.com/slu-openGIS/areal/issues/16)), all of which are fixed on the current GitHub master branch:
 
@@
 The simplest workaround is to install the development version of `areal` from GitHub.
+3.
+Interpolation fails if the `sf` geometry column is not named `geometry`.
+The simplest workaround is to either rename the column to `geometry` before executing `aw_interpolate()`.
+Alternatively, you can install the development version of `areal` from GitHub.
+4.
+Interpolation with `output = "tibble"` only returns the identification number and the estimated value.
+If you want other variables from the target data, the simplest workaround is to join the output to the original target data.
+Alternatively, you can install the development version of `areal` from GitHub.
 
-Big thanks to early adopter [Matt Herman](https://github.com/mfherman) for catching both of these!
+Big thanks to early adopter [Matt Herman](https://github.com/mfherman) for catching the first two and [David Blodgett](https://github.com/dblodgett-usgs) for catching the third!
 

### 2019-03-22 index.Rmd

--- 2019-01-01 index.Rmd
@@
 ## Bug Fixes in v0.1.3
-The initial CRAN release contains two known bugs (see Issues [6](https://github.com/slu-openGIS/areal/issues/6) and [7](https://github.com/slu-openGIS/areal/issues/7)), both of which are fixed in the current GitHub release:
+The initial CRAN release contains four known bugs (see Issues [6](https://github.com/slu-openGIS/areal/issues/6), [7](https://github.com/slu-openGIS/areal/issues/7), [14](https://github.com/slu-openGIS/areal/issues/14), and [16](https://github.com/slu-openGIS/areal/issues/16)), all of which are fixed on the current GitHub master branch:
 

### 2019-03-22 R/aw_intersect.R
And actually add the st_geometry_type call.

@@ -65,7 +65,7 @@ aw_intersect <- function(.data, source, areaVar) {
   intersection %>%
     aw_area(areaVar = !!areaVarQ) -> intersection
 
-  if(any(grepl("GEOMETRY", intersection))) {
+  if(any(grepl("GEOMETRY", sf::st_geometry_type(intersection)))) {
     intersection <- sf::st_collection_extract(intersection) %>%
       sf::st_cast("MULTIPOLYGON")
   }

### 2019-03-22 tests/testthat/test_aw_intersect.R
test for GEOMETRYCOLLECTION cast to MULTIPOLYGON

@@ -32,3 +32,9 @@ test_that("correctly specified functions execute without error", {
   expect_error(aw_intersect(ar_stl_wards, source = ar_stl_race, areaVar = "area"), NA)
   expect_error(aw_intersect(ar_stl_wards, source = ar_stl_race, areaVar = area), NA)
 })
+
+test_that("GEOMETRY check casts to MULTIPOLYGON when ", {
+  load("data/areal_intersect_test.rda")
+  intersection <- aw_intersect(si_zcta, si_tract, "area")
+  expect(all(sf::st_geometry_type(intersection) == "MULTIPOLYGON"))
+})

### 2019-03-22 paper/response_to_reviewers.md
work on revisions

We would like to thank both @edzer and @sjsrey as well as @lheagy for the feedback and the opportunity to revise both the software and the manuscript.

## Reviewer 1 - @edzer
* The pdf of the paper shows R code on page 2, but this code is hidden where it runs off the page at the side.
    * The example has been changed to return a tibble object rather than an `sf` object. A new line was added below the example that clarifies the `sf` functionality as well.

* The manuscript claims it provides functions that "validate data suitability for areal interpolation", but does not explain what this validation does. What does it do?
    * A description of the validation process has been added to the manuscript in the section titled **The `areal` R package**.

* given that the package does little more than sf::st_interpolate_aw, and given that that function was available first, the added value of the packages would become more clear when it would mention the name of that function (rather than refer to "the existing functionality in sf"),
    * A direct reference to `sf::st_interpolate_aw` in the first paragraph of the section titled **The `areal` R package**.

* show in a side-by-side comparison that areal::aw_interpolate and sf::st_interpolate_aw give identical results for an intensive an an extensive variable

* give an example where areal::aw_interpolate does something different when there is a difference in areas, and show how large the effect of doing this is

* the correct reference for Pebesma, E. (2018) is found here
    * This has been corrected

* change the wording of "black box", as this is not a black box. Closed source software is a black box

* the areal-weighted-interpolation vignette mentions "Spatially intensive operations are used when the data to be interpolated are a ratio." I'm afraid it is not this simple: a counter example is is CO2 emissions measured in tons/year: an extensive variable when interpolated spatially.

* Additionally, @edzer provided [feedback](https://github.com/slu-openGIS/areal/issues/18) about two packages listed as dependencies that may not be necessary.
    * Both `lwgeom` and `tibble` have been removed as dependencies

### 2019-03-22 paper/appendix_code.R

@@ -1,0 +1,88 @@
+# comparisons with `sf`
+library(areal)
+library(dplyr)
+library(microbenchmark)
+library(sf)
+
+# areal package, spatially extensive using total
+areal_exT <- aw_interpolate(ar_stl_wards, tid = WARD, source = ar_stl_race, sid = GEOID,
+               weight = "total", output = "tibble", extensive = "TOTAL_E")
+
+# areal package, spatially extensive using sum
+areal_exS <- aw_interpolate(ar_stl_wards, tid = WARD, source = ar_stl_race, sid = GEOID,
+                            weight = "sum", output = "tibble", extensive = "TOTAL_E")
+
+# areal package, spatially intensive
+areal_in <- aw_interpolate(ar_stl_wards, tid = WARD, source = ar_stl_asthma, sid = GEOID,
+                            weight = "sum", output = "tibble", intensive = "ASTHMA")
+
+# sf package, spatially extensive
+sf_ex <- st_interpolate_aw(ar_stl_race["TOTAL_E"], ar_stl_wards, extensive = TRUE)
+
+# sf package, spatially intensive
+sf_in <- st_interpolate_aw(ar_stl_asthma["ASTHMA"], ar_stl_wards, extensive = FALSE)
+
+# compile results
+areal_exS <- areal_exS %>%
+  select(WARD, TOTAL_E) %>%
+  rename(areal_exS = TOTAL_E)
+
+areal_exT <- areal_exT %>%
+  select(WARD, TOTAL_E) %>%
+  rename(areal_exT = TOTAL_E)
+
+sf_ex <- sf_ex %>%
+  rename(sf_ex = TOTAL_E)
+st_geometry(sf_ex) <- NULL
+
+extensive <- left_join(sf_ex, areal_exT, by = c("Group.1" = "WARD")) %>%
+  left_join(., areal_exS, by = c("Group.1" = "WARD")) %>%
+  mutate(delta = areal_exT-areal_exS) %>%
+  rename(Ward = Group.1) %>%
+  as_tibble()
+
+areal_in <- areal_in %>%
+  select(WARD, ASTHMA) %>%
+  rename(areal_in = ASTHMA)
+
+sf_in <- sf_in %>%
+  rename(sf_in = ASTHMA)
+st_geometry(sf_in) <- NULL
+
+intensive <- left_join(sf_in, areal_in, by = c("Group.1" = "WARD")) %>%
+  rename(Ward = Group.1) %>%
+  as_tibble()
+
[…]

### 2019-03-23 R/aw_interpolate.R
address issues with two vectors in mixed interpolations

@@ -220,7 +220,7 @@ aw_interpolate <- function(.data, tid, source, sid, weight = "sum", output = "sf
     } else if (length(intensive) > 1){
 
       # interpolate
-      inresults <- aw_interpolate_multiple(source = source, sid = !!sidQ, values = extensive, target = .data,
+      inresults <- aw_interpolate_multiple(source = source, sid = !!sidQ, values = intensive, target = .data,
                                            tid = !!tidQ, type = "intensive", weight = "sum")
 
     }

### 2019-03-23 paper/response_to_reviewers.md
update paper manuscript, vignettes

@@
 We would like to thank both @edzer and @sjsrey as well as @lheagy for the feedback and the opportunity to revise both the software and the manuscript.
+We believe that the manuscript has been greatly strengthened as a result of your collective feedback and are excited to resubmit it for your review.
 
@@
 
-* show in a side-by-side comparison that areal::aw_interpolate and sf::st_interpolate_aw give identical results for an intensive an an extensive variable
+* show in a side-by-side comparison that areal::aw_interpolate and sf::st_interpolate_aw give identical results for an intensive an extensive variable
+    * This is included in the new **A Quick Comparison with sf** section with two figures, one for extensive interpolations and one for intensive interpolations.
 
 * give an example where areal::aw_interpolate does something different when there is a difference in areas, and show how large the effect of doing this is
+    * This is included in the new **A Quick Comparison with sf** section with a figure and a description of the difference as well as why one approach may be preferable over the other.
 
@@
 * change the wording of "black box", as this is not a black box. Closed source software is a black box
+    * This has been changed to:
+
+    > "for users who need to unpack the interpolation workflow"
 
 * the areal-weighted-interpolation vignette mentions "Spatially intensive operations are used when the data to be interpolated are a ratio." I'm afraid it is not this simple: a counter example is is CO2 emissions measured in tons/year: an extensive variable when interpolated spatially.
+    * This has been changed to:
+
+    > "Spatially *intensive* operations are used when the data to be interpolated are, for example, a percentage or density value."
 
@@
     * Both `lwgeom` and `tibble` have been removed as dependencies
+
+## Reviewer 2 - @sjsrey
+
+* Scaling: the current examples are well crafted and illustrate the core functionality.
+At the same time n is fairly modest here and one wonders if these methods were going to be used for larger n problems, or applied iteratively over many cities , would there be any bottlenecks users should be aware of?
+    * We have added benchmarks to the end a new section titled **Performance Notes** as well as a discussion of a special case that `areal` handles, which is when geometry collections are returned by `sf::st_intersection()`.
+The process for handling this special case is more resource intensive and results in longer processing times.
+
+* The distinction between extensive and intensive variables is handled nicely.
+One case that might also be considered is the choice between interpolation of an intensive variable directly versus deriving the intensive estimates as a ratio of two extensive variables that have been estimated
+    * Mindful of the short length of JOSS manuscripts, we have included a discussion of this in the vignette on areal weighted interpolation in the section entitled **Mixed Interpolations**.
+
+* The weight argument names are a bit confusing.
+    * Since the package is already on CRAN, we are reluctant to change the argument.
+In the paper, however, we have made two clarifications to address this.
+The first was to explicitly link the names for both weights to their descriptions in the second to last paragraph of the section **The areal R package**.
+They now read:
+
+    > "...we offer a formula that matches the existing functionality in `sf`, which is based on the total area of the original source feature (specified with `weight = "total"`)."
+
+    > "This uses a sum of the source feature areas remaining after the data are intersected as part of the spatial weight calculation process (specified with `weight = "sum"`)."
+
+    We also have added a section titled **A Quick Comparison with sf** that illustrates the difference between these two approaches, and includes a brief discussion of the selection process between both in the second and third full paragraphs.
+It includes the following language:
+
+    > "If we expect that our source and target data should overlap completely (but perhaps do not because of data quality issues), the `"sum"` approach will allocate all individuals into target features whereas `"total"` will not because it uses the total area of each source feature."

### 2019-03-23 paper/appendix_code.R

@@ -1,6 +1,7 @@
 # comparisons with `sf`
 library(areal)
 library(dplyr)
+library(gridExtra)
 library(microbenchmark)
 library(sf)
 
@@ -53,11 +54,44 @@ intensive <- left_join(sf_in, areal_in, by = c("Group.1" = "WARD")) %>%
   rename(Ward = Group.1) %>%
   as_tibble()
 
+extensiveSub <- extensive %>%
+  filter(Ward >= 1 & Ward <= 10) %>%
+  mutate(
+    sf_ex = round(sf_ex, digits = 3),
+    areal_exT = round(areal_exT, digits = 3),
+    areal_exS = round(areal_exS, digits = 3),
+    delta = round(delta, digits = 3)
+  ) %>%
+  rename(
+    `sf` = sf_ex,
+    `areal, total weight` = areal_exT,
+    `areal, sum weight` = areal_exS
+  )
+
+intensiveSub <- intensive %>%
+  filter(Ward >= 1 & Ward <= 10) %>%
+  mutate(
+    sf_in = round(sf_in, digits = 3),
+    areal_in = round(areal_in, digits = 3)
+  ) %>%
+  rename(
+    `sf` = sf_in,
+    `areal` = areal_in
+  )
+
+png(filename = "paper/extensiveTable.png", width = 480, height = 300, bg = "white", type = "cairo-png")
+grid.arrange(tableGrob(extensiveSub, rows = NULL), top = "Comparison of sf and areal Output\nSpatially Extensive Interpolation")
+dev.off()
+
+png(filename = "paper/intensiveTable.png", width = 480, height = 300, bg = "white", type = "cairo-png")
+grid.arrange(tableGrob(intensiveSub, rows = NULL), top = "Comparison of sf and areal Output\nSpatially Intensive Interpolation")
+dev.off()
+
 # compare spatially extensive interpolations
 microbenchmark(
   aw_interpolate(ar_stl_wards, tid = WARD, source = ar_stl_race, sid = GEOID,
                  weight = "total", output = "tibble", extensive = "TOTAL_E"),
-  st_interpolate_aw(ar_stl_race["TOTAL_E"], ar_stl_wards, extensive = TRUE)
+  suppressWarnings(st_interpolate_aw(ar_stl_race["TOTAL_E"], ar_stl_wards, extensive = TRUE))
 )
 
 # Unit: milliseconds
@@ -74,7 +108,7 @@ microbenchmark(
 microbenchmark(
[…]

### 2019-03-23 README.Rmd
add notes about additional bug fixes

@@
 `sf`) frameworks.
+
+## Bug Fixes in v0.1.4
+There are two additional bug fixes in v0.1.4:
+
+1.
+Data that do not require being converted back from a geometry collection (see #2 in the next section) were still being processed through this code, making runtimes longer than necessary.
+This has been fixed.
+2.
+Mixed interpolations with multiple extensive and intensive variables would get incorrect output containing two copies of the extensive results.
+This has been fixed, and the simplest workaround is to install the development version of `areal` from GitHub.
 

### 2019-03-24 paper/response_to_reviewers.md
add appendix and updated manuscript

@@
 
-    > "If we expect that our source and target data should overlap completely (but perhaps do not because of data quality issues), the `"sum"` approach will allocate all individuals into target features whereas `"total"` will not because it uses the total area of each source feature."
+    > "If we expect that our source and target data should overlap completely (but perhaps do not because of data quality issues), the `"sum"` approach will allocate all individuals into target features whereas `"total"`will not, instead allocating only a proportion of individuals relative to the overlap between the source and target features.
+In the example data provided in the `areal` package, this is the case - the Census tracts do not perfectly map onto the extent of the wards, and so the `"total"` approach is inappropriate."

### 2019-03-24 paper/appendix.Rmd
add appendix and updated manuscript

---
title: "Appendix for JOSS Paper"
author: "Christopher Prener, Ph.D."
date: '(`r format(Sys.time(), "%B %d, %Y")`)'
output: 
  github_document: default
  html_notebook: default 
---

## Introduction
This document contains replication code for the examples provided in our *Journal of Open Source Software* manuscript.

## Dependencies
This notebook requires

```{r load-packages}
# primary package
library(areal)

# tidyverse packages
library(dplyr)

# spatial packages
library(sf)
library(tidycensus)
library(tigris)

# other packages
library(gridExtra)
library(microbenchmark)
library(testthat)
```

## Comparisons with `sf`
### Produce Estimates
First, we'll create three spatially extensive estimates for comparison. Two will use the `areal` package, varying the type of weight applied to the estimate:

```{r areal-extensive}
# areal package, spatially extensive using total
areal_exT <- aw_interpolate(ar_stl_wards, tid = WARD, source = ar_stl_race, sid = GEOID,
               weight = "total", output = "tibble", extensive = "TOTAL_E")

# areal package, spatially extensive using sum
areal_exS <- aw_interpolate(ar_stl_wards, tid = WARD, source = ar_stl_race, sid = GEOID,
                            weight = "sum", output = "tibble", extensive = "TOTAL_E")
```

Next, we'll replicate the process using `sf`:

```{r sf-extensive}
# sf package, spatially extensive
sf_ex <- st_interpolate_aw(ar_stl_race["TOTAL_E"], ar_stl_wards, extensive = TRUE)
```

We'll also produce a spatially intensive estimate using `areal`:

```{r areal-intensive}
# areal package, spatially intensive
areal_in <- aw_interpolate(ar_stl_wards, tid = WARD, source = ar_stl_asthma, sid = GEOID,
                            weight = "sum", output = "tibble", intensive = "ASTHMA")
```

And finally, we'll replicate the spatially intensive estimate using `sf`:

```{r sf-intensive}
# sf package, spatially intensive
sf_in <- st_interpolate_aw(ar_stl_asthma["ASTHMA"], ar_stl_wards, extensive = FALSE)
```

### Compile Results
First, we'll compile the extensive results:

```{r compile-extensive}
# areal, extensive sum
areal_exS <- areal_exS %>%
  select(WARD, TOTAL_E) %>%
  rename(areal_exS = TOTAL_E)

# areal, extensive total
areal_exT <- areal_exT %>%
  select(WARD, TOTAL_E) %>%
  rename(areal_exT = TOTAL_E)

# sf, extensive total
sf_ex <- sf_ex %>%
  rename(sf_ex = TOTAL_E)
st_geometry(sf_ex) <- NULL

# combine
extensive <- left_join(sf_ex, areal_exT, by = c("Group.1" = "WARD")) %>%
  left_join(., areal_exS, by = c("Group.1" = "WARD")) %>%
  mutate(delta = areal_exT-areal_exS) %>%
  rename(Ward = Group.1) %>%
  as_tibble()
```

We'll make a similar compliation of the intensive results:

```{r compile-intensive}
# areal, intensive
areal_in <- areal_in %>%
  select(WARD, ASTHMA) %>%
  rename(areal_in = ASTHMA)

# sf, intensive
sf_in <- sf_in %>%
  rename(sf_in = ASTHMA)
st_geometry(sf_in) <- NULL

# combine
intensive <- left_join(sf_in, areal_in, by = c("Group.1" = "WARD")) %>%
  rename(Ward = Group.1) %>%
  as_tibble()
```

### Print Tables
The following code chunk produces two tables for the manuscript:

```{r print-tables}
# produce rounded extensive estimates
extensiveSub <- extensive %>%
  filter(Ward >= 1 & Ward <= 10) %>%
  mutate(
    sf_ex = round(sf_ex, digits = 3),
    areal_exT = round(areal_exT, digits = 3),
    areal_exS = round(areal_exS, digits = 3),
    delta = round(delta, digits = 3)
  ) %>%
  rename(
    `sf` = sf_ex,
    `areal, total weight` = areal_exT,
    `areal, sum weight` = areal_exS
  )

# print extensive table
png(filename = "paper/extensiveTable.png", width = 480, height = 300, bg = "white", type = "cairo-png")
grid.arrange(tableGrob(extensiveSub, rows = NULL), top = "Comparison of sf and areal Output\nSpatially Extensive Interpolation")
dev.off()

# produce rounded intensive estimates
intensiveSub <- intensive %>%
  filter(Ward >= 1 & Ward <= 10) %>%
  mutate(
    sf_in = round(sf_in, digits = 3),
    areal_in = round(areal_in, digits = 3)
  ) %>%
  rename(
    `sf` = sf_in,
    `areal` = areal_in
  )

# print intensive table
png(filename = "paper/intensiveTable.png", width = 480, height = 300, bg = "white", type = "cairo-png")
grid.arrange(tableGrob(intensiveSub, rows = NULL), top = "Comparison of sf and areal Output\nSpatially Intensive Interpolation")
dev.off()
```

### Compare Results
We can verify that the `areal` workflow with `weight = "total"` matches the `sf` extensive output:

```{r verify-extensive}
expect_equal(extensive$sf_ex, extensive$areal_exT)
```

We can do the same for the intensive interpolations:

```{r verify-intensive}
expect_equal(intensive$sf_in, intensive$areal_in)
```

### Benchmark
Next, we'll benchmark the extensive estimation times:

```{r extensive-benchmark}
# compare spatially extensive interpolations
microbenchmark(
  aw_interpolate(ar_stl_wards, tid = WARD, source = ar_stl_race, sid = GEOID,
                 weight = "total", output = "tibble", extensive = "TOTAL_E"),
  suppressWarnings(st_interpolate_aw(ar_stl_race["TOTAL_E"], ar_stl_wards, extensive = TRUE))
)
```

We'll repeat the process for the intensive estimations:

```{r intensive-benchmark}
# compare spatially intensive interpolations
microbenchmark(
  aw_interpolate(ar_stl_wards, tid = WARD, source = ar_stl_asthma, sid = GEOID,
                 weight = "sum", output = "tibble", intensive = "ASTHMA"),
  suppressWarnings(st_interpolate_aw(ar_stl_asthma["ASTHMA"], ar_stl_wards, extensive = FALSE))
)
```

## Geometry Collections
Finally, we'll provide an example of a more intensive estimation process that also triggers the geometry collection workflow, which will add to the estimation time. We need to download several data sets using `tigris` and `tidycensus`:

```{r download-census, include=FALSE}
# county populations
moPop <- get_acs(geography = "county", variables = "B01003_001", output = "wide", state = 29, geometry = TRUE) %>%
  st_transform(crs = 26915) %>%
  select(GEOID, B01003_001E) %>%
  rename(totalPop = B01003_001E)

# block group geometry
moBlockGroups <- block_groups(state = 29, class = "sf") %>%
  st_transform(crs = 26915) %>%
  select(GEOID)
```

Here are the sample sizes for both data sets:

```{r census-n}
nrow(moPop)
nrow(moBlockGroups)
```

Here is the benchmark for the estimates produced with these data:

```{r benchmark-geo-collection}
microbenchmark(
  aw_interpolate(moBlockGroups, tid = GEOID, source = moPop, sid = GEOID,
                 weight = "sum", output = "tibble", intensive = "totalPop")
)
```

### 2019-05-20 README.Rmd
updates to README and pkgdown site

--- 2019-01-02 README.Rmd
@@
 [![DOI](https://zenodo.org/badge/152279647.svg)](https://zenodo.org/badge/latestdoi/152279647) 
+[![DOI](http://joss.theoj.org/papers/10.21105/joss.01221/status.svg)](https://doi.org/10.21105/joss.01221)
 [![CRAN_status_badge](http://www.r-pkg.org/badges/version/areal)](https://cran.r-project.org/package=areal)
@@
 
-## Bug Fixes in v0.1.3
-The initial CRAN release contains two known bugs (see Issues [6](https://github.com/slu-openGIS/areal/issues/6) and [7](https://github.com/slu-openGIS/areal/issues/7)), both of which are fixed on the current GitHub master branch:
+### *Joural of Open Souce Software* Article
+An [article](http://joss.theoj.org/papers/10.21105/joss.01221) describing `areal`'s approach to areal weighted interpolation has been published in the [*The Journal of Open Source Software*](http://joss.theoj.org/).
+The article includes benchmarking of `areal` performance on several data sets.
+Please [cite the paper](/inst/CITATION) if you use `areal` in your work!
 
-1.
-If the `tid` and `sid` column names are identical, the interpolated column created by `aw_interpolate()` will consist of all `NA` values.
-The simplest workaround is to rename either `tid` or `sid` before executing `aw_interpolate()`.
-Alternatively, you can install the development version of `areal` from GitHub.
-2.
-Some intersections of `sf` geometries will result in geometry collections being created.
-This appears to be an infrequent issue, but it will result in an error when `aw_interpolate()` is executed.
-The error will begin with `Warning in st_cast.GEOMETRYCOLLECTION(X[[i]], ...)`.
-The simplest workaround is to install the development version of `areal` from GitHub.
-
-Big thanks to early adopter [Matt Herman](https://github.com/mfherman) for catching both of these!
+### What is New in v0.1.4.5?
+This version of `areal` contains all of the bug fixes that were identified by early adaopters after the initial CRAN submission.
+Special thanks to [Matt Herman](https://github.com/mfherman) and [David Blodgett](https://github.com/dblodgett-usgs) for their issues and pull requests!
+Check out the [NEWS file](/NEWS.md) for details on all of the bugs that were identified.
 

### 2019-05-20 index.Rmd
updates to README and pkgdown site

--- 2019-01-01 index.Rmd
@@
 [![Coverage status](https://codecov.io/gh/slu-openGIS/areal/branch/master/graph/badge.svg)](https://codecov.io/github/slu-openGIS/areal?branch=master)
+[![DOI](https://zenodo.org/badge/152279647.svg)](https://zenodo.org/badge/latestdoi/152279647) 
+[![DOI](http://joss.theoj.org/papers/10.21105/joss.01221/status.svg)](https://doi.org/10.21105/joss.01221)
 [![CRAN_status_badge](http://www.r-pkg.org/badges/version/areal)](https://cran.r-project.org/package=areal)
@@
 
-## Bug Fixes in v0.1.3
-The initial CRAN release contains two known bugs (see Issues [6](https://github.com/slu-openGIS/areal/issues/6) and [7](https://github.com/slu-openGIS/areal/issues/7)), both of which are fixed on the current GitHub master branch:
+### *Joural of Open Souce Software* Article
+An [article](http://joss.theoj.org/papers/10.21105/joss.01221) describing `areal`'s approach to areal weighted interpolation has been published in the [*The Journal of Open Source Software*](http://joss.theoj.org/).
+The article includes benchmarking of `areal` performance on several data sets.
+Please [cite the paper](/docs/authors.html) if you use `areal` in your work!
 
-1.
-If the `tid` and `sid` column names are identical, the interpolated column created by `aw_interpolate()` will consist of all `NA` values.
-The simplest workaround is to rename either `tid` or `sid` before executing `aw_interpolate()`.
-Alternatively, you can install the development version of `areal` from GitHub.
-2.
-Some intersections of `sf` geometries will result in geometry collections being created.
-This appears to be an infrequent issue, but it will result in an error when `aw_interpolate()` is executed.
-The error will begin with `Warning in st_cast.GEOMETRYCOLLECTION(X[[i]], ...)`.
-The simplest workaround is to install the development version of `areal` from GitHub.
-
-Big thanks to early adopter [Matt Herman](https://github.com/mfherman) for catching both of these!
+### What is New in v0.1.4.5?
+This version of `areal` contains all of the bug fixes that were identified by early adaopters after the initial CRAN submission.
+Special thanks to [Matt Herman](https://github.com/mfherman) and [David Blodgett](https://github.com/dblodgett-usgs) for their issues and pull requests!
+Check out the [Changelog](/docs/news/index.html) for details on all of the bugs that were identified.
 

### 2019-05-20 index.Rmd
get links working correctly on pkgdown homepage

@@
 The article includes benchmarking of `areal` performance on several data sets.
-Please [cite the paper](/docs/authors.html) if you use `areal` in your work!
+Please [cite the paper](authors.html) if you use `areal` in your work!
 
@@
 Special thanks to [Matt Herman](https://github.com/mfherman) and [David Blodgett](https://github.com/dblodgett-usgs) for their issues and pull requests!
-Check out the [Changelog](/docs/news/index.html) for details on all of the bugs that were identified.
+Check out the [Changelog](news/index.html) for details on all of the bugs that were identified.
 

### 2020-05-11 R/ar_tessellate.R
prepare for dplyr release

@@ -58,7 +58,7 @@ ar_tessellate <- function(.data, shape = "square", size = 1){
 
   # make tessellation, clip to original boundary and convert to sf/df
   tess <- sf::st_make_grid(.data, cellsize, square = shape) %>%
-    sf::st_intersection(sf::st_union(.data)) %>% sf::st_sf()
+    suppressWarnings(sf::st_intersection(sf::st_union(.data))) %>% sf::st_sf()
 
   return(tess)
 }

### 2020-05-11 R/aw_calculate.R

@@ -80,14 +80,14 @@ aw_calculate <- function(.data, value, areaWeight, newVar){
   # check variables
   if(!!valsQN %in% colnames(.data) == FALSE) {
     stop(glue::glue("Variable '{var}', given for the value, cannot be found in the given intersected object.",
-                    var = valsQ))
+                    var = valsQN))
   }
 
   if (!!areaWeightQN != "...areaWeight"){
 
     if(!!areaWeightQN %in% colnames(.data) == FALSE) {
       stop(glue::glue("Variable '{var}', given for the area weight, cannot be found in the given intersected object.",
-                      var = areaWeightQ))
+                      var = areaWeightQN))
     }
 
   }

### 2020-05-11 R/aw_interpolate.R

@@ -252,9 +252,7 @@ aw_interpolate <- function(.data, tid, source, sid, weight = "sum", output = "sf
 
   # rename tid
   if (nameConflict == TRUE){
-
     out <- dplyr::rename(out, !!tidOrig := !!tidQN)
-
   }
 
   # return output
@@ -367,9 +365,15 @@ aw_interpolate_multiple <- function(source, sid, values, target, tid, type, weig
     split(values) %>%
     purrr::map(~ aw_strip_df(source, id = !!sidQ, value = .x)) %>%
     purrr::imap(~ aw_interpolater(source = .x, sid = !!sidQ, value = (!! rlang::quo(!! rlang::sym(.y))),
-                                  target = targetS, tid = !!tidQ, type = type, weight = weight)) %>%
-    purrr::reduce(.f = dplyr::bind_cols) %>%
-    dplyr::select(dplyr::one_of(colNames)) -> out
+                                  target = targetS, tid = !!tidQ, type = type, weight = weight,
+                                  multiple = TRUE)) %>%
+    purrr::reduce(.f = dplyr::bind_cols) -> out
+
+  # remove geometry
+  sf::st_geometry(targetS) <- NULL
+
+  # combine
+  out <- dplyr::bind_cols(targetS, out)
 
   # return output
   return(out)
@@ -443,7 +447,7 @@ aw_strip_df <- function(.data, id, value){
 # @return A \code{sf} object or tibble with \code{value} interpolated into
 #    the \code{target} data.
 #
-aw_interpolater <- function(source, sid, value, target, tid, type, weight) {
+aw_interpolater <- function(source, sid, value, target, tid, type, weight, multiple = FALSE) {
 
   # save parameters to list
   paramList <- as.list(match.call())
@@ -483,6 +487,11 @@ aw_interpolater <- function(source, sid, value, target, tid, type, weight) {
 
   # remove sf from output
   sf::st_geometry(out) <- NULL
+
+  # fix multiples
+  if (multiple == TRUE){
+    out <- dplyr::select(out, !!valueQ)
+  }
 
   # return target output
   return(out)

### 2020-05-11 R/aw_preview_weights.R

@@ -91,12 +91,12 @@ aw_preview_weights <- function(.data, tid, source, sid, type){
   # check variables
   if(!!sidQN %in% colnames(source) == FALSE) {
     stop(glue::glue("Variable '{var}', given for the source ID ('sid'), cannot be found in the given source object.",
-                    var = sidQ))
+                    var = sidQN))
   }
 
   if(!!tidQN %in% colnames(.data) == FALSE) {
     stop(glue::glue("Variable '{var}', given for the target ID ('tid'), cannot be found in the given target object.",
-                    var = tidQ))
+                    var = tidQN))
   }
 
   # validate source and target data

### 2020-05-11 R/aw_total.R

@@ -113,14 +113,14 @@ aw_total <- function(.data, source, id, areaVar, totalVar, type, weight){
   # check variables
   if(!!idQN %in% colnames(.data) == FALSE) {
     stop(glue::glue("Variable '{var}', given for the ID ('id'), cannot be found in the given intersected object.",
-                    var = idQ))
+                    var = idQN))
   }
 
   if (!!areaVarQN != "...area"){
 
     if(!!areaVarQN %in% colnames(.data) == FALSE) {
       stop(glue::glue("Variable '{var}', given for the area, cannot be found in the given intersected object.",
-                      var = areaVarQ))
+                      var = areaVarQN))
     }
 
   }

### 2020-05-11 R/aw_weight.R

@@ -87,7 +87,7 @@ aw_weight <- function(.data, areaVar, totalVar, areaWeight){
 
     if(!!areaVarQN %in% colnames(.data) == FALSE) {
       stop(glue::glue("Variable '{var}', given for the area, cannot be found in the given intersected object.",
-                      var = areaVarQ))
+                      var = areaVarQN))
     }
 
   }
@@ -96,7 +96,7 @@ aw_weight <- function(.data, areaVar, totalVar, areaWeight){
 
     if(!!totalVarQN %in% colnames(.data) == FALSE) {
       stop(glue::glue("Variable '{var}', given for the total area, cannot be found in the given intersected object.",
-                      var = totalVarQ))
+                      var = totalVarQN))
     }
 
   }

### 2020-05-11 inst/extdata/sandbox.R

@@ -1,0 +1,17 @@
+devtools::load_all()
+
+# target data
+data(ar_stl_wards, package = "areal")
+
+# source data
+data(ar_stl_race, package = "areal")
+
+# calculate intersection
+ar_stl_wards %>%
+  aw_intersect(source = ar_stl_race, areaVar = "...area") %>%
+  aw_total(source = ar_stl_race, id = GEOID, areaVar = "...area",
+           totalVar = "...totalArea", weight = "sum", type = "extensive") %>%
+  aw_weight(areaVar = "...area", totalVar = "...totalArea", areaWeight = "...areaWeight") %>%
+  aw_calculate(value = "TOTAL_E", areaWeight = "...areaWeight") -> intersect
+
+aw_aggregate(intersect, target = ar_stl_wards, tid = ham, interVar = "TOTAL_E")

### 2020-05-11 tests/testthat/test_aw_interpolate.R

@@ -122,10 +122,10 @@ test_that("interpolated values are equal", {
 })
 
 test_that("classes are created appropriately", {
-  expect_equal("sf", class(totalResult1)[1])
-  expect_equal("tbl_df", class(totalResult2)[1])
-  expect_equal("sf", class(asthmaResult)[1])
-  expect_equal("tbl_df", class(mixedResult)[1])
+  expect_equal("sf" %in% class(totalResult1), TRUE)
+  expect_equal("tbl_df" %in% class(totalResult2), TRUE)
+  expect_equal("sf" %in% class(asthmaResult), TRUE)
+  expect_equal("tbl_df" %in% class(mixedResult), TRUE)
 })
 
 # test inputs not otherwise tested above ------------------------------------------------

### 2020-05-11 tests/testthat/test_aw_intersect.R

@@ -39,5 +39,5 @@ load(system.file("testdata", "geometryCollection.rda", package = "areal", mustWo
 
 test_that("GEOMETRY check casts to MULTIPOLYGON when necessary", {
   intersection <- aw_intersect(si_zcta, si_tract, "area")
-  expect(all(sf::st_geometry_type(intersection) == "MULTIPOLYGON"))
+  expect_equal(all(sf::st_geometry_type(intersection) == "MULTIPOLYGON"), TRUE)
 })

### 2020-05-11 README.Rmd
update logo and version number
update ci pipeline

@@
 
-### What is New in v0.1.4.5?
-This version of `areal` contains all of the bug fixes that were identified by early adaopters after the initial CRAN submission.
-Special thanks to [Matt Herman](https://github.com/mfherman) and [David Blodgett](https://github.com/dblodgett-usgs) for their issues and pull requests!
-Check out the [NEWS file](/NEWS.md) for details on all of the bugs that were identified.
+### What is New in v0.1.6?
+This version contains updates under the hood to make it compatible with `dplyr`'s v1.0 release!
 

### 2020-05-11 README.Rmd
update documentation

@@
 [![Coverage status](https://codecov.io/gh/slu-openGIS/areal/branch/master/graph/badge.svg)](https://codecov.io/github/slu-openGIS/areal?branch=master)
+[![CRAN_status_badge](http://www.r-pkg.org/badges/version/areal)](https://cran.r-project.org/package=areal)
+[![cran checks](https://cranchecks.info/badges/worst/areal)](https://cran.r-project.org/web/checks/check_results_areal.html)
+[![Downloads](http://cranlogs.r-pkg.org/badges/areal?color=brightgreen)](http://www.r-pkg.org/pkg/areal)
 [![DOI](https://zenodo.org/badge/152279647.svg)](https://zenodo.org/badge/latestdoi/152279647) 
 [![DOI](http://joss.theoj.org/papers/10.21105/joss.01221/status.svg)](https://doi.org/10.21105/joss.01221)
-[![CRAN_status_badge](http://www.r-pkg.org/badges/version/areal)](https://cran.r-project.org/package=areal)
 

### 2020-05-11 README.Rmd
fix travis url

--- 2020-05-11 README.Rmd
@@
 [![lifecycle](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://www.tidyverse.org/lifecycle/#maturing)
-[![Travis-CI Build Status](https://travis-ci.org/slu-openGIS/areal.svg?branch=master)](https://travis-ci.org/slu-openGIS/areal)
+[![Travis-CI Build Status](https://travis-ci.com/slu-openGIS/areal.svg?branch=master)](https://travis-ci.com/slu-openGIS/areal)
 [![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/slu-openGIS/areal?branch=master&svg=true)](https://ci.appveyor.com/project/chris-prener/areal)
 [![Coverage status](https://codecov.io/gh/slu-openGIS/areal/branch/master/graph/badge.svg)](https://codecov.io/github/slu-openGIS/areal?branch=master)
+[![CRAN_status_badge](http://www.r-pkg.org/badges/version/areal)](https://cran.r-project.org/package=areal)
+[![cran checks](https://cranchecks.info/badges/worst/areal)](https://cran.r-project.org/web/checks/check_results_areal.html)
+[![Downloads](http://cranlogs.r-pkg.org/badges/areal?color=brightgreen)](http://www.r-pkg.org/pkg/areal)
 [![DOI](https://zenodo.org/badge/152279647.svg)](https://zenodo.org/badge/latestdoi/152279647) 
 [![DOI](http://joss.theoj.org/papers/10.21105/joss.01221/status.svg)](https://doi.org/10.21105/joss.01221)
-[![CRAN_status_badge](http://www.r-pkg.org/badges/version/areal)](https://cran.r-project.org/package=areal)
 

### 2020-05-12 R/ar_tessellate.R
ar_tesselate now passes checks

@@ -57,16 +57,17 @@ ar_tessellate <- function(.data, shape = "square", size = 1){
   shape <- switch(shape, "square" = TRUE, "hexagon" = FALSE)
 
   # unionize original boundary
-  boundary <- sf::st_union(.data)
+  suppressWarnings(boundary <- sf::st_union(.data))
 
   # make tessellation, clip to original boundary and convert to sf/df
   grid <- sf::st_make_grid(.data, cellsize, square = shape)
-  suppressWarnings({
-    tess <- sf::st_intersection(grid, boundary)
-  })
+  tess <- sf::st_intersection(grid, boundary)
 
   # coerce to sf from sfc
+
+
   tess <- sf::st_sf(tess)
+
 
   return(tess)
 }

### 2020-05-12 README.Rmd
address winbuilder NOTES

@@
 ## Contributor Code of Conduct
-Please note that this project is released with a [Contributor Code of Conduct](.github/CODE_OF_CONDUCT.md). By participating in this project you agree to abide by its terms.
+Please note that this project is released with a [Contributor Code of Conduct](https://slu-opengis.github.io/areal/CODE_OF_CONDUCT.html).
+By participating in this project you agree to abide by its terms.

### 2020-07-20 R/aw_intersect.R
no longer require specific geometry col names

@@ -97,10 +97,14 @@ aw_area <- function(.data, areaVar){
   # nse
   areaVarQN <- rlang::quo_name(rlang::enquo(areaVar))
 
-
-
   # calculate area
-  out <- dplyr::mutate(.data, !!areaVarQN := unclass(sf::st_area(geometry)))
+  calculated_area <- unclass(sf::st_area(.data))
+
+  # join
+  out <- cbind(.data, calculated_area)
+
+  # rename
+  out <- dplyr::rename(out, !!areaVarQN := calculated_area)
 
   # return output
   return(out)

### 2020-07-20 tests/testthat/test_aw_interpolate.R
add unit test to address issue

@@ -140,6 +140,14 @@ test_that("correctly specified functions execute without error", {
                               intensive = c("ASTHMA", "ASTHMA2")), NA)
 })
 
+race_geom <- dplyr::rename(ar_stl_race, geom = geometry)
+
+test_that("correctly specified functions execute without error", {
+  expect_error(aw_interpolate(ar_stl_wards, tid = WARD, source = race_geom, sid = GEOID,
+                              weight = "sum", output = "sf", extensive = c("TOTAL_E", "WHITE_E", "BLACK_E")), NA)
+})
+
+
 # test for matching sid and tid ------------------------------------------------
 
 wardsGEOID <- dplyr::rename(ar_stl_wards, GEOID = WARD)

### 2022-05-29 README.Rmd
update documentation
update badges

@@
 
-[![lifecycle](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://www.tidyverse.org/lifecycle/#maturing)
-[![Travis-CI Build Status](https://travis-ci.com/slu-openGIS/areal.svg?branch=master)](https://travis-ci.com/slu-openGIS/areal)
-[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/slu-openGIS/areal?branch=master&svg=true)](https://ci.appveyor.com/project/chris-prener/areal)
-[![Coverage status](https://codecov.io/gh/slu-openGIS/areal/branch/master/graph/badge.svg)](https://codecov.io/github/slu-openGIS/areal?branch=master)
+[![R build status](https://github.com/slu-openGIS/areal/workflows/R-CMD-check/badge.svg)](https://github.com/slu-openGIS/areal/actions)
+[![Coverage status](https://codecov.io/gh/slu-openGIS/areal/branch/master/graph/badge.svg)](https://codecov.io/github/slu-openGIS/areal?branch=main)
 [![CRAN_status_badge](http://www.r-pkg.org/badges/version/areal)](https://cran.r-project.org/package=areal)
@@
 Please [cite the paper](/inst/CITATION) if you use `areal` in your work!
-
-### What is New in v0.1.6?
-This version contains updates under the hood to make it compatible with `dplyr`'s v1.0 release!
 

### 2022-05-29 README.Rmd
replace http with https

@@
 [![Coverage status](https://codecov.io/gh/slu-openGIS/areal/branch/master/graph/badge.svg)](https://codecov.io/github/slu-openGIS/areal?branch=main)
-[![CRAN_status_badge](http://www.r-pkg.org/badges/version/areal)](https://cran.r-project.org/package=areal)
+[![CRAN_status_badge](https://www.r-pkg.org/badges/version/areal)](https://cran.r-project.org/package=areal)
 [![cran checks](https://cranchecks.info/badges/worst/areal)](https://cran.r-project.org/web/checks/check_results_areal.html)
-[![Downloads](http://cranlogs.r-pkg.org/badges/areal?color=brightgreen)](http://www.r-pkg.org/pkg/areal)
+[![Downloads](https://cranlogs.r-pkg.org/badges/areal?color=brightgreen)](https://www.r-pkg.org/pkg/areal)
 [![DOI](https://zenodo.org/badge/152279647.svg)](https://zenodo.org/badge/latestdoi/152279647) 
-[![DOI](http://joss.theoj.org/papers/10.21105/joss.01221/status.svg)](https://doi.org/10.21105/joss.01221)
+[![DOI](https://joss.theoj.org/papers/10.21105/joss.01221/status.svg)](https://doi.org/10.21105/joss.01221)
 
@@
 ### *Joural of Open Souce Software* Article
-An [article](http://joss.theoj.org/papers/10.21105/joss.01221) describing `areal`'s approach to areal weighted interpolation has been published in the [*The Journal of Open Source Software*](http://joss.theoj.org/).
+An [article](https://joss.theoj.org/papers/10.21105/joss.01221) describing `areal`'s approach to areal weighted interpolation has been published in the [*The Journal of Open Source Software*](https://joss.theoj.org/).
 The article includes benchmarking of `areal` performance on several data sets.

### 2022-05-29 R/aw_interpolate.R
resolve issue with defaults (#37)

@@ -73,14 +73,6 @@ aw_interpolate <- function(.data, tid, source, sid, weight = "sum", output = "sf
     stop("A variable name must be specified for the 'sid' argument.")
   }
 
-  if (missing(weight)) {
-    stop("A weight type (either 'sum' or 'total') must be specified for the 'weight' argument.")
-  }
-
-  if (missing(output)) {
-    stop("An output type (either 'tibble' or 'sf') must be specified for the 'output' argument.")
-  }
-
   # determine extensive and intensive
   if (missing(extensive) & missing(intensive)){
     stop("Either 'extensive' or 'intenstive' must be specified with an accompanying list of variables to interpolate.")

### 2022-05-29 tests/testthat/test_aw_interpolate.R

@@ -54,12 +54,6 @@ test_that("errors with missing parameters", {
                               weight = "sum", output = "sf", extensive = "TOTAL_E"),
                "A variable name must be specified for the 'sid' argument.")
   expect_error(aw_interpolate(ar_stl_wards, tid = WARD, source = ar_stl_race, sid = GEOID,
-                              output = "sf", extensive = "TOTAL_E"),
-               "A weight type \\(either 'sum' or 'total'\\) must be specified for the 'weight' argument.")
-  expect_error(aw_interpolate(ar_stl_wards, tid = WARD, source = ar_stl_race, sid = GEOID,
-                              weight = "sum", extensive = "TOTAL_E"),
-               "An output type \\(either 'tibble' or 'sf'\\) must be specified for the 'output' argument.")
-  expect_error(aw_interpolate(ar_stl_wards, tid = WARD, source = ar_stl_race, sid = GEOID,
                               weight = "sum", output = "sf"),
                "Either 'extensive' or 'intenstive' must be specified with an accompanying list of variables to interpolate.")
 })

### 2022-05-30 inst/extdata/createData.R
resave test data as older object

@@ -52,4 +52,4 @@ rm(stlRace, stlTracts, ar_stl_race, ar_stl_wards, ar_stl_asthma, ar_stl_wardsCli
 totalCompare1 <- aw_interpolate(ar_stl_wards, tid = WARD, source = ar_stl_race, sid = GEOID,
                                weight = "sum", output = "sf", extensive = "TOTAL_E")
 
-save(totalCompare1, file = "inst/testdata/totalCompare1.rda")
+save(totalCompare1, file = "inst/testdata/totalCompare1.rda", version = 2)

### 2022-05-30 README.Rmd
update links to chris-prener

@@
 
-[![R build status](https://github.com/slu-openGIS/areal/workflows/R-CMD-check/badge.svg)](https://github.com/slu-openGIS/areal/actions)
-[![Coverage status](https://codecov.io/gh/slu-openGIS/areal/branch/master/graph/badge.svg)](https://codecov.io/github/slu-openGIS/areal?branch=main)
+[![R build status](https://github.com/chris-prener/areal/workflows/R-CMD-check/badge.svg)](https://github.com/chris-prener/areal/actions)
+[![Coverage status](https://codecov.io/gh/chris-prener/areal/branch/master/graph/badge.svg)](https://codecov.io/github/chris-prener/areal?branch=main)
 [![CRAN_status_badge](https://www.r-pkg.org/badges/version/areal)](https://cran.r-project.org/package=areal)
@@
 ## Installation
-### Installing Dependencies
-You should check the [`sf` package website](https://r-spatial.github.io/sf/) and the [`areal` package website](https://slu-openGIS.github.io/areal/) for the latest details on installing dependencies for that package.
-Instructions vary significantly by operating system.
-For best results, have `sf` installed before you install `areal`.
-Other dependencies, like `dplyr`, will be installed automatically with `areal` if they are not already present.
-
-The one exception here is the dependency `lwgeom`, which Linux users will need to follow some [special instructions](https://github.com/r-spatial/lwgeom) to install correctly.
-
-### Installing areal
 The easiest way to get `areal` is to install it from CRAN:
@@
 # install.packages("remotes")
-remotes::install_github("slu-openGIS/areal")
+remotes::install_github("chris-prener/areal")
 ```
+
+Note that installations that require `sf` to be built from *source* will require additional software regardless of operating system.
+You should check the [`sf` package website](https://r-spatial.github.io/sf/) for the latest details on installing dependencies for that package.
+Instructions vary significantly by operating system.
 
@@
 `areal` currently implements an approach to interpolation known as areal weighted interpolation.
-It is arguably the simplest and most common approach to areal interpolation, though it does have some drawbacks (see the [areal weighted interpolation vignette](https://slu-opengis.github.io/areal/articles/areal-weighted-interpolation.html) for details).
+It is arguably the simplest and most common approach to areal interpolation, though it does have some drawbacks (see the [areal weighted interpolation vignette](https://chris-prener.github.io/areal/articles/areal-weighted-interpolation.html) for details).
 The basic usage of `areal` is through the `aw_interpolate()` function.
@@
 This example outputs a simple features (`sf`) object and uses one of two options for calculating weights.
-All of these arguments are documented both within the package (use `?aw_interpolate`) and on the [package's website](https://slu-opengis.github.io/areal/).
+All of these arguments are documented both within the package (use `?aw_interpolate`) and on the [package's website](https://chris-prener.github.io/areal/).
 
@@
 Functions for validating data, previewing the areal weights, and walking step-by-step through the interpolation process are provided.
-See the [areal weighted interpolation vignette](https://slu-opengis.github.io/areal/articles/areal-weighted-interpolation.html) for additional details about this workflow.
+See the [areal weighted interpolation vignette](https://chris-prener.github.io/areal/articles/areal-weighted-interpolation.html) for additional details about this workflow.
 
@@
 
-- [Pycnophylactic method](https://github.com/slu-openGIS/areal/issues/1) (raster based, eliminates the sharp transitions in value between target features)
-- [Binary dasymetric method](https://github.com/slu-openGIS/areal/issues/2) (incorporates ancillary data so that population is not assumed to be evenly distributed within units)
-- [3-class regression dasymetric method](https://github.com/slu-openGIS/areal/issues/3) (allows for a more complex estimation based on multiple forms of ancillary data)
+- [Pycnophylactic method](https://github.com/chris-prener/areal/issues/1) (raster based, eliminates the sharp transitions in value between target features)
+- [Binary dasymetric method](https://github.com/chris-prener/areal/issues/2) (incorporates ancillary data so that population is not assumed to be evenly distributed within units)
+- [3-class regression dasymetric method](https://github.com/chris-prener/areal/issues/3) (allows for a more complex estimation based on multiple forms of ancillary data)
 
@@
 ## Contributor Code of Conduct
-Please note that this project is released with a [Contributor Code of Conduct](https://slu-opengis.github.io/areal/CODE_OF_CONDUCT.html).
+Please note that this project is released with a [Contributor Code of Conduct](https://chris-prener.github.io/areal/CODE_OF_CONDUCT.html).
 By participating in this project you agree to abide by its terms.
